---
title: "Statistical analysis of behavioral tasks  paramters"
output:
  pdf_document: default
  html_document: default
date: "2025-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(results="asis")
knitr::opts_chunk$set(warning = FALSE)
```



## Overview

This notebook tests whether tDCS (sham, unilateral, bilateral) affects behavioral performance across four motor tasks: **APM** (Arm Position Matching), **VGR** (Visually Guided Reaching), **OH** (Object Hit), and **BOB** (Ball on Bar).

Analysis pipeline:

1. **Omnibus test**: within-subject permutation LMER F-test (`param ~ stimulation_condition + (1|subject)`) for each behavioral parameter, with condition labels shuffled within each subject.
2. **Post-hoc**: paired permutation t-tests for the three pairwise comparisons (unilateral vs sham, bilateral vs sham, bilateral vs unilateral), with Bonferroni correction applied within each parameter.
3. **Learning effect check**: LMER F-test (`param ~ session_no + (1|subject)`) to verify no session-order effects.
4. **Plots**: boxplots of key significant parameters saved to `PLOTS_OUTPUT_DIR`.



```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(ggplot2)
library(dplyr)
library(janitor)
library(ggpubr)
library(rstatix)
library(tidyverse)
library(gtsummary)
library(knitr)
library(ggrepel)
library(rstatix)
library(sjPlot)
library(sjtable2df)
library(GGally)
library(MKinfer)
library(lme4)
library(lmerTest)
library(dplyr)
library(knitr)
library(emmeans)
library(knitr)
library(gt)
```


# LMER permutation F-tets  

## Perm F-test functions

```{r}
get_perm_f_val_task_parmas <- function(data, param_list, n_perm = 1000,
                                        print_progress = TRUE, seed = 123) {
  # Fixed columns / reference
  subject_col <- "subject"
  condition_col <- "stimulation_condition"
  ref_level <- "sham"

  # Store base seed for parameter-specific seeding
  base_seed <- seed

  # Ensure factor with reference level
  data[[condition_col]] <- relevel(as.factor(data[[condition_col]]), ref = ref_level)

  results_df <- data.frame(
    parameter = character(),
    f_statistic = numeric(),
    df_num = numeric(),
    df_denom = numeric(),
    p_value = numeric(),
    n_valid_perms = integer(),
    n_obs = integer(),
    singular_warnings = integer(),
    original_singular = logical(),
    significance = character(),
    stringsAsFactors = FALSE
  )

  for (i in seq_along(param_list)) {
    param <- param_list[i]
    
    # Set parameter-specific seed for reproducibility
    if (!is.null(base_seed)) {
      set.seed(base_seed + i - 1)
    }
    
    if (print_progress) {
      cat("##########################\n")
      cat("Within-Subject Permutation Test for:", param, "\n")
      if (!is.null(base_seed)) {
        cat("Seed:", base_seed + i - 1, "\n")
      }
    }

    # formula y ~ condition + (1|subject)
    formula <- as.formula(sprintf("%s ~ %s + (1|%s)", param, condition_col, subject_col))
    if (print_progress) cat("Formula:", deparse(formula), "\n")

    # Select data for this parameter (no outlier removal)
    model_df <- data %>%
      dplyr::select(dplyr::all_of(c(subject_col, condition_col, param))) %>%
      dplyr::filter(!is.na(.data[[param]]))  # Only remove missing values

    n_obs <- nrow(model_df)
    n_subjects <- dplyr::n_distinct(model_df[[subject_col]])

    if (print_progress) {
      cat("Total observations:", n_obs, "\n")
      cat("Number of subjects:", n_subjects, "\n")
    }

    # Check if enough data
    if (n_obs == 0 || n_subjects < 2) {
      if (print_progress) cat("Not enough data. Skipping", param, "\n\n")
      results_df <- rbind(
        results_df,
        data.frame(
          parameter = param,
          f_statistic = NA_real_,
          df_num = NA_real_,
          df_denom = NA_real_,
          p_value = NA_real_,
          n_valid_perms = 0L,
          n_obs = n_obs,
          singular_warnings = NA_integer_,
          original_singular = NA,
          significance = "ns",
          stringsAsFactors = FALSE
        )
      )
      next
    }

    # Call permutation (uses current RNG state from set.seed above)
    perm_result <- permutation_test_lmer(
      formula = formula,
      data = model_df,
      group_var = condition_col,
      subject_col = subject_col,
      n_perm = n_perm
    )

    sig_level <- ifelse(perm_result$p_value < 0.001, "***",
                 ifelse(perm_result$p_value < 0.01,  "**",
                 ifelse(perm_result$p_value < 0.05,  "*", "ns")))

    results_df <- rbind(
      results_df,
      data.frame(
        parameter = param,
        f_statistic = perm_result$original_f,
        df_num = perm_result$df_num,
        df_denom = perm_result$df_denom,
        p_value = perm_result$p_value,
        n_valid_perms = perm_result$n_valid_perms,
        n_obs = n_obs,
        singular_warnings = perm_result$singular_warnings,
        original_singular = perm_result$original_singular,
        significance = sig_level,
        stringsAsFactors = FALSE
      )
    )

    if (print_progress) {
      cat("\n")
      cat("Original model singular:", perm_result$original_singular, "\n")
      cat("Singular warnings in permutations:", perm_result$singular_warnings, "out of", n_perm, "\n")
      cat("Original F-statistic:", perm_result$original_f, "\n")
      cat("Permutation p-value:", perm_result$p_value, "\n")
      cat("Valid permutations:", perm_result$n_valid_perms, "out of", n_perm, "\n")
      cat("Significance:", sig_level, "\n\n")
    }
  }

  results_df
}

permutation_test_lmer <- function(formula, data, group_var, subject_col, n_perm = 1000) {
  # Fit original model and capture singularity warning
  original_singular <- FALSE
  original_model <- tryCatch({
    withCallingHandlers(
      lme4::lmer(formula, data = data, REML = FALSE),
      warning = function(w) {
        if (grepl("singular", w$message, ignore.case = TRUE)) {
          original_singular <<- TRUE
        }
      }
    )
  }, error = function(e) {
    stop("Error fitting original model: ", e$message)
  })

  anova_tbl      <- anova(original_model)
  original_fstat <- anova_tbl$`F value`[1]
  # df_num: always k-1 conditions (robust to anova table column name differences)
  df_num         <- nlevels(data[[group_var]]) - 1L
  # df_denom: Satterthwaite via lmerTest (convert without refitting)
  lt_anova       <- tryCatch(
    anova(lmerTest::as_lmerModLmerTest(original_model)),
    error = function(e) NULL
  )
  df_denom       <- if (!is.null(lt_anova) && "DenDF" %in% names(lt_anova)) lt_anova$DenDF[1] else NA_real_

  # Permutation test: shuffle group labels WITHIN each subject
  perm_fstats <- numeric(n_perm)
  singular_count <- 0L

  for (i in seq_len(n_perm)) {
    perm_data <- data %>%
      dplyr::group_by(!!dplyr::sym(subject_col)) %>%
      dplyr::mutate(
        !!dplyr::sym(group_var) := sample(.data[[group_var]])
      ) %>%
      dplyr::ungroup()

    # Fit permuted model and record F (handle singular fits/warnings)
    tryCatch({
      withCallingHandlers(
        {
          perm_model <- lme4::lmer(formula, data = perm_data, REML = FALSE)
          perm_fstats[i] <- anova(perm_model)$`F value`[1]
        },
        warning = function(w) {
          if (grepl("singular", w$message, ignore.case = TRUE)) {
            singular_count <<- singular_count + 1L
          }
        }
      )
    }, error = function(e) {
      perm_fstats[i] <- NA_real_
    })
  }

  # Remove NAs and compute p-value (right-tail, as F is larger = more extreme)
  perm_fstats <- perm_fstats[!is.na(perm_fstats)]
  p_value <- mean(perm_fstats >= original_fstat, na.rm = TRUE)

  list(
    original_f = original_fstat,
    df_num = df_num,
    df_denom = df_denom,
    p_value = p_value,
    n_valid_perms = length(perm_fstats),
    singular_warnings = singular_count,
    original_singular = original_singular
  )
}
```


## Global params

Global number of permutations and dirs

```{r}
library(dotenv)
load_dot_env(file = "../.env")

N_PERM = 10000

BASE_DIR    <- Sys.getenv("BASE_DIR")
RESULTS_DIR <- Sys.getenv("RESULTS_DIR")
BEH_DATA_ANON_DIR <- Sys.getenv("BEH_DATA_ANON_DIR")

INPUT_DIR <- file.path(BEH_DATA_ANON_DIR, "csv")
OUTPUT_DIR <- file.path(RESULTS_DIR, "stats", "01_behavioral_tasks")
PLOTS_OUTPUT_DIR <- file.path(RESULTS_DIR, "main_figures", "04_behavioral_tasks")

dir.create(OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
dir.create(PLOTS_OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
```

## APM 


Left hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR, "APM_left_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR, "APM_left_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR, "APM_left_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()
comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))
comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness, 
                                  stimulation_condition, active_arm,  
                                  abs_error_x_m, 
                                  abs_error_y_m, 
                                  variability_x_m,
                                  variability_y_m,
                                  contraction_expansion_ratio_x,
                                  contraction_expansion_ratio_y,
                                  shift_x_m,
                                  shift_y_m)
#comb_data <- comb_data %>% rename(contra_expa_ratio_xy = contraction_expansion_ratio_xy)
comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$stimulation_condition <- factor(comb_data$stimulation_condition, levels = c("sham", "ua-tDCS", "bi-tDCS"))

comb_data_l <- comb_data
table(comb_data_l$stimulation_condition)
head(comb_data_l)
```

Righ hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR,"APM_right_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR,"APM_right_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR,"APM_right_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()
comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))



comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, 
                                         fraction_complete, handedness,
                                         stimulation_condition, active_arm,
                                         abs_error_x_m, 
                                          abs_error_y_m, 
                                          variability_x_m,
                                          variability_y_m,
                                          contraction_expansion_ratio_x,
                                          contraction_expansion_ratio_y,
                                          shift_x_m,
                                          shift_y_m)


#comb_data <- comb_data %>% rename(contra_expa_ratio_xy = contraction_expansion_ratio_xy)
comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$stimulation_condition <- factor(comb_data$stimulation_condition, levels = c("sham", "ua-tDCS", "bi-tDCS"))

comb_data_r <- comb_data
table(comb_data_r$stimulation_condition)
head(comb_data_r)
```

```{r}
conatinated_apm <- rbind(comb_data_l, comb_data_r)
head(conatinated_apm)
tail(conatinated_apm)
str(conatinated_apm)
```

```{r}
apm_wide <- conatinated_apm %>%
  mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH")) %>%
  pivot_wider(
    id_cols = c("subject", "neuron_id", "handedness",
                "session_no","stimulation_condition"),
    names_from = arm_prefix,
    values_from = c(
      "fraction_complete", 
      "abs_error_x_m",
      "abs_error_y_m",
      "variability_x_m",
      "variability_y_m",
      "contraction_expansion_ratio_x",
      "contraction_expansion_ratio_y",
      "shift_x_m",
      "shift_y_m"
    ),
    names_glue = "{arm_prefix}_{.value}"
  )

str(apm_wide)

head(apm_wide)
```

```{r, results='hide'}
apm_behavior_vars <- c(
  "abs_error_x_m",
  "abs_error_y_m",
  "variability_x_m",
  "variability_y_m",
  "contraction_expansion_ratio_x",
  "contraction_expansion_ratio_y",
  "shift_x_m",
  "shift_y_m"
  )

apm_behavior_vars_lh <- paste0("LH_", apm_behavior_vars)
apm_behavior_vars_rh <- paste0("RH_", apm_behavior_vars)

# Combine both LH and RH behavior variables
apm_behavior_vars_both_hands <- c(apm_behavior_vars_lh, apm_behavior_vars_rh)
```


```{r}
apm_permutation_results <- get_perm_f_val_task_parmas(
  data = apm_wide,
  param_list = apm_behavior_vars_both_hands,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(as.data.frame(apm_permutation_results), digits = 4)
```


## VGR 

Left hand
```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR,"VGR_left_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR,"VGR_left_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR,"VGR_left_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)


comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness, 
                                  stimulation_condition, active_arm,  
                                  posture_speed_m_s, 
                                  reaction_time_s,
                                  initial_direction_angle_rad,
                                  initial_distance_ratio,
                                  initial_speed_ratio,
                                  speed_maxima_count,
                                  movement_time_s,
                                  path_length_ratio,
                                  false_starts)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$stimulation_condition <- factor(comb_data$stimulation_condition, levels = c("sham", "ua-tDCS", "bi-tDCS"))

comb_data_l <- comb_data
table(comb_data_l$stimulation_condition)
head(comb_data_l)
```

Right hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR,"VGR_right_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR,"VGR_right_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR,"VGR_right_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness, 
                                  stimulation_condition, active_arm, 
                                  posture_speed_m_s, 
                                  reaction_time_s,
                                  initial_direction_angle_rad,
                                  initial_distance_ratio,
                                  initial_speed_ratio,
                                  speed_maxima_count,
                                  movement_time_s,
                                  path_length_ratio,
                                  false_starts)


comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$stimulation_condition <- factor(comb_data$stimulation_condition, levels = c("sham", "ua-tDCS", "bi-tDCS"))

comb_data_r <- comb_data
table(comb_data_r$stimulation_condition)
head(comb_data_r)
```

```{r}
conatinated_vgr <- rbind(comb_data_l, comb_data_r)
head(conatinated_vgr)
tail(conatinated_vgr)
str(conatinated_vgr)
```

```{r}
vgr_wide <- conatinated_vgr %>%
  mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH")) %>%
  pivot_wider(
    id_cols = c("subject", "neuron_id", "handedness", 
                "session_no", "stimulation_condition"),
    names_from = arm_prefix,
    values_from = c("fraction_complete", 
                    "posture_speed_m_s", 
                    "reaction_time_s", 
                    "initial_direction_angle_rad", 
                    "initial_distance_ratio", 
                    "initial_speed_ratio", 
                    "speed_maxima_count",
                    "movement_time_s", 
                    "path_length_ratio", 
                    "false_starts"
    ),
    names_glue = "{arm_prefix}_{.value}"
  )

str(vgr_wide)

head(vgr_wide)
```

```{r, results='hide'}
vgr_behavior_vars <- c("posture_speed_m_s", 
                       "reaction_time_s", 
                       "initial_direction_angle_rad", 
                       "initial_distance_ratio", 
                       "initial_speed_ratio", 
                       "speed_maxima_count",
                       "movement_time_s", 
                       "path_length_ratio", 
                       "false_starts")

vgr_behavior_vars_lh <- paste0("LH_", vgr_behavior_vars)
vgr_behavior_vars_rh <- paste0("RH_", vgr_behavior_vars)

# Combine both LH and RH behavior variables
vgr_behavior_vars_both_hands <- c(vgr_behavior_vars_lh, vgr_behavior_vars_rh)
```


```{r}
vgr_permutation_results <- get_perm_f_val_task_parmas(
  data = vgr_wide,
  param_list = vgr_behavior_vars_both_hands,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(vgr_permutation_results)
```

## BOB

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR,"BOB_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR,"BOB_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR,"BOB_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness, 
                                  stimulation_condition, active_arm, 
                                  x1_targets_completed,
                                  x2_targets_completed,
                                  x3_targets_completed,
                                  #x2_drops,#variance=0
                                  x3_drops,#
                                  #x2_drops_targets,##variance=0
                                  x3_drops_targets,#
                                  x1_mean_movement_time_s,
                                  x2_mean_movement_time_s,
                                  x3_mean_movement_time_s,
                                  x1_right_hand_speed_maxima,
                                  x2_right_hand_speed_maxima,
                                  x3_right_hand_speed_maxima,
                                  x1_left_hand_speed_maxima,
                                  x2_left_hand_speed_maxima,
                                  x3_left_hand_speed_maxima,
                                  x1_mean_bar_angle_rad,
                                  x2_mean_bar_angle_rad,
                                  x3_mean_bar_angle_rad,
                                  x1_bar_length_variability,#
                                  x2_bar_length_variability,#
                                  x3_bar_length_variability,#
                                  x1_reaction_time_abs_diff_s,
                                  x1_hand_speed_diff_m_s,
                                  x2_hand_speed_diff_m_s,
                                  x3_hand_speed_diff_m_s,
                                  x1_mean_right_hand_speed_m_s,
                                  x2_mean_right_hand_speed_m_s, 
                                  x3_mean_right_hand_speed_m_s,
                                  x1_mean_left_hand_speed_m_s,
                                  x2_mean_left_hand_speed_m_s, 
                                  x3_mean_left_hand_speed_m_s, 
                                  x1_mean_bar_angle_rad,
                                  x2_mean_bar_angle_rad,
                                  x3_mean_bar_angle_rad,
                                  x1_stdev_bar_angle_rad,
                                  x2_stdev_bar_angle_rad,
                                  x3_stdev_bar_angle_rad,
                                  x1_norm_absolute_hand_speed_diff,
                                  x2_norm_absolute_hand_speed_diff,
                                  x3_norm_absolute_hand_speed_diff,
                                  x1_hand_speed_peak_bias,
                                  x2_hand_speed_peak_bias,
                                  x3_hand_speed_peak_bias,
                                  x1_hand_path_bias,
                                  x2_hand_path_bias,
                                  x3_hand_path_bias 
                                  )

bob_behavior_vars <- c(
  "x1_targets_completed",
  "x2_targets_completed",
  "x3_targets_completed",
  #"x2_drops", #variance=0
  "x3_drops",
  #"x2_drops_targets", #variance=0
  "x3_drops_targets",
  "x1_mean_movement_time_s",
  "x2_mean_movement_time_s",
  "x3_mean_movement_time_s",
  "x1_right_hand_speed_maxima",
  "x2_right_hand_speed_maxima",
  "x3_right_hand_speed_maxima",
  "x1_left_hand_speed_maxima",
  "x2_left_hand_speed_maxima",
  "x3_left_hand_speed_maxima",
  "x1_mean_bar_angle_rad",
  "x2_mean_bar_angle_rad",
  "x3_mean_bar_angle_rad",
  "x1_bar_length_variability",
  "x2_bar_length_variability",
  "x3_bar_length_variability",
  "x1_reaction_time_abs_diff_s",
  "x1_hand_speed_diff_m_s",
  "x2_hand_speed_diff_m_s",
  "x3_hand_speed_diff_m_s", 
  "x1_mean_right_hand_speed_m_s",
  "x2_mean_right_hand_speed_m_s", 
  "x3_mean_right_hand_speed_m_s",
  "x1_mean_left_hand_speed_m_s",
  "x2_mean_left_hand_speed_m_s", 
  "x3_mean_left_hand_speed_m_s",
  "x1_mean_bar_angle_rad",
  "x2_mean_bar_angle_rad",
  "x3_mean_bar_angle_rad",
  "x1_stdev_bar_angle_rad",
  "x2_stdev_bar_angle_rad",
  "x3_stdev_bar_angle_rad",
  "x1_norm_absolute_hand_speed_diff",
  "x2_norm_absolute_hand_speed_diff",
  "x3_norm_absolute_hand_speed_diff",
  "x1_hand_speed_peak_bias",
  "x2_hand_speed_peak_bias",
  "x3_hand_speed_peak_bias",
  "x1_hand_path_bias",
  "x2_hand_path_bias",
  "x3_hand_path_bias" 
)

# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(across(all_of(bob_behavior_vars), as.numeric))

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$stimulation_condition <- factor(comb_data$stimulation_condition, levels = c("sham", "ua-tDCS", "bi-tDCS"))

bob_data <- comb_data
table(bob_data$stimulation_condition)
head(bob_data)
```

```{r}
bob_permutation_results <- get_perm_f_val_task_parmas(
  data = bob_data,
  param_list = bob_behavior_vars,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(bob_permutation_results)
```

## OH
```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR,"OH_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR,"OH_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR,"OH_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% select(neuron_id, session_no, fraction_complete, 
                                  handedness, stimulation_condition, active_arm, 
                                  total_hits,
                                  hits_with_left,
                                  hits_with_right,
                                  hand_bias_of_hits,
                                  median_error,
                                  miss_bias,
                                  hand_speed_right_m_s,
                                  hand_speed_left_m_s,
                                  hand_speed_bias,
                                  movement_area_right_hand_m_2, 
                                  movement_area_left_hand_m_2,
                                  movement_area_bias,
                                  hand_transition,
                                  hand_selection_overlap)

oh_behavior_vars <- c("total_hits", 
                   "hits_with_left", 
                   "hits_with_right", 
                   "hand_bias_of_hits",
                   "median_error", 
                   "miss_bias", 
                   "hand_speed_right_m_s",
                   "hand_speed_left_m_s", 
                   "hand_speed_bias", 
                   "movement_area_right_hand_m_2", 
                   "movement_area_left_hand_m_2", 
                   "movement_area_bias", 
                   "hand_transition",
                   "hand_selection_overlap")

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$stimulation_condition <- factor(comb_data$stimulation_condition, levels = c("sham", "ua-tDCS", "bi-tDCS"))

# Verifying the result
oh_data <- comb_data
table(oh_data$stimulation_condition)
head(oh_data)
```
```{r}
oh_permutation_results <- get_perm_f_val_task_parmas(
  data = oh_data,
  param_list = oh_behavior_vars,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(oh_permutation_results)
```

## Save results 
```{r}
# Save omnibus F-test results
write.csv(apm_permutation_results, file.path(OUTPUT_DIR,"perm_F_results_apm.csv"), row.names = FALSE)
write.csv(vgr_permutation_results, file.path(OUTPUT_DIR,"perm_F_results_vgr.csv"), row.names = FALSE)
write.csv(bob_permutation_results, file.path(OUTPUT_DIR,"perm_F_results_bob.csv"), row.names = FALSE)
write.csv(oh_permutation_results,  file.path(OUTPUT_DIR,"perm_F_results_oh.csv"),  row.names = FALSE)
```


# Post-hoc permutation t-tests 

## Perm pair-wise t-tests function
```{r}
# ============================================================================
# POST-HOC PERMUTATION T-TESTS FUNCTIONS
# ============================================================================

# Function to perform pairwise permutation t-tests with correction
perform_pairwise_tests <- function(
  task_df,
  task_params,
  n_perm = 5000,
  correction_method = "bonferroni"
) {
  # NO seeding here - relies on parent function setting RNG state
  
  subject_col <- "subject"
  condition_col <- "stimulation_condition"

  # Comparisons (order matters for reporting)
  comparisons <- list(
    c("ua-tDCS", "sham"),
    c("bi-tDCS", "sham"),
    c("bi-tDCS", "ua-tDCS")
  )

  # Container for all parameters
  results_df <- data.frame(
    parameter = character(),
    comparison = character(),
    n_pairs = integer(),
    df = integer(),
    statistic = numeric(),
    p_value = numeric(),
    p_corrected = numeric(),
    cohens_d = numeric(),
    significance = character(),
    stringsAsFactors = FALSE
  )

  for (param in task_params) {

    # Collect this parameter's three pairwise tests
    param_results <- data.frame(
      parameter = character(),
      comparison = character(),
      n_pairs = integer(),
      df = integer(),
      statistic = numeric(),
      p_value = numeric(),
      cohens_d = numeric(),
      stringsAsFactors = FALSE
    )

    for (comp in comparisons) {
      cond1 <- comp[1]
      cond2 <- comp[2]

      # 1) Subset to the two conditions + subject + current param
      sub_df <- task_df[task_df[[condition_col]] %in% c(cond1, cond2),
                        c(subject_col, condition_col, param)]
      names(sub_df) <- c(subject_col, condition_col, "y")

      # 2) Wide by condition to align pairs by subject
      wide <- tidyr::pivot_wider(
        sub_df,
        id_cols = tidyselect::all_of(subject_col),
        names_from = tidyselect::all_of(condition_col),
        values_from = "y"
      )

      # Keep only rows where both conditions are present (paired)
      if (!all(c(cond1, cond2) %in% names(wide))) {
        data1 <- numeric(0)
        data2 <- numeric(0)
      } else {
        wide <- wide[stats::complete.cases(wide[, c(cond1, cond2), drop = FALSE]), , drop = FALSE]
        data1 <- wide[[cond1]]
        data2 <- wide[[cond2]]
      }

      # If too few pairs, store NA row
      if (length(data1) < 2L) {
        param_results <- rbind(param_results,
          data.frame(
            parameter = param,
            comparison = paste(cond1, "vs", cond2),
            n_pairs = length(data1),
            df = NA_integer_,
            statistic = NA_real_,
            p_value = NA_real_,
            cohens_d = NA_real_,
            stringsAsFactors = FALSE
          )
        )
        next
      }

      # 3) Permutation paired t-test (uses current RNG state)
      perm_test <- perm.t.test(data1, data2, paired = TRUE, R = n_perm)

      # 4) Cohen's d for paired data
      dvals <- data1 - data2
      cohens_d_val <- mean(dvals, na.rm = TRUE) / stats::sd(dvals, na.rm = TRUE)

      # 5) Collect results
      param_results <- rbind(param_results,
        data.frame(
          parameter = param,
          comparison = paste(cond1, "vs", cond2),
          n_pairs = length(dvals),
          df = length(dvals) - 1L,
          statistic = unname(perm_test$statistic),
          p_value = unname(perm_test$p.value),
          cohens_d = cohens_d_val,
          stringsAsFactors = FALSE
        )
      )
    }

    # 6) Multiple-comparison correction within this parameter (across its 3 tests)
    param_results$p_corrected <- stats::p.adjust(param_results$p_value, method = correction_method)

    # 7) Significance marks (prioritize corrected p; then fallback to raw p and trend)
    param_results$significance <- ifelse(!is.na(param_results$p_corrected) & param_results$p_corrected < 0.05, "**",
                                  ifelse(!is.na(param_results$p_value)     & param_results$p_value     < 0.05, "*",
                                  ifelse(!is.na(param_results$p_value)     & param_results$p_value     < 0.10, ".", "")))

    # 8) Append to all results
    results_df <- rbind(results_df,
                        param_results[, c("parameter","comparison","n_pairs","df","statistic","p_value","p_corrected","cohens_d","significance")])
  }

  # Significant-only view
  sig_results <- subset(results_df, significance %in% c(".", "*", "**"))

  list(
    all_results = results_df,
    significant_results = sig_results
  )
}


# Post-hoc permutation t-tests (paired) for significant F-tests
run_posthoc_permutation <- function(
  f_results_df,
  task_df,
  alpha = 0.05,
  n_perm = 5000,
  seed = 123,
  correction_method = "bonferroni"
) {
  
  base_seed <- seed
  subject_col   <- "subject"
  condition_col <- "stimulation_condition"

  # Which parameters are significant at the omnibus level
  sig_params <- f_results_df$parameter[f_results_df$p_value < alpha]
  
  if (length(sig_params) == 0L) {
    message("No parameters passed the F-test threshold; nothing to run post-hoc on.")
    return(list(all = data.frame(), by_param = list()))
  }

  all_posthoc <- list()

  for (i in seq_along(sig_params)) {
    param <- sig_params[i]
    
    # Set seed ONCE for this parameter (covers all 3 comparisons)
    if (!is.null(base_seed)) {
      set.seed(base_seed + i - 1)
    }
    
    # Use all data (no outlier removal)
    filtered_df <- task_df

    # Run the paired permutation post-hoc comparisons for THIS param only
    ph <- perform_pairwise_tests(
      task_df = filtered_df,
      task_params = param, 
      n_perm = n_perm,
      correction_method = correction_method
    )

    all_posthoc[[param]] <- ph$all_results
  }

  combined <- do.call(rbind, all_posthoc)

  # Return both a combined df and split-by-parameter list
  list(
    all = combined[order(combined$parameter, combined$comparison), ],
    by_param = all_posthoc
  )
}
```

## APM

```{r}
apm_posthoc <- run_posthoc_permutation(
  f_results_df = apm_permutation_results,
  task_df = apm_wide,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "bonferroni"  
)
apm_posthoc$all
```

## VGR
```{r}
vgr_posthoc <- run_posthoc_permutation(
  f_results_df = vgr_permutation_results,
  task_df = vgr_wide,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "fdr"  
)
vgr_posthoc$all
```

## BOB
```{r}
bob_posthoc <- run_posthoc_permutation(
  f_results_df = bob_permutation_results,
  task_df = bob_data,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "bonferroni"  
)
bob_posthoc$all
```

## OH 
```{r}
oh_posthoc <- run_posthoc_permutation(
  f_results_df = oh_permutation_results,
  task_df = oh_data,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "bonferroni"  
)
oh_posthoc$all
```


## Save Results 
```{r}
# Save posthoc test results
write.csv(apm_posthoc$all, file.path(OUTPUT_DIR,"perm_posthoc_apm.csv"), row.names = FALSE)
write.csv(vgr_posthoc$all, file.path(OUTPUT_DIR,"perm_posthoc_vgr.csv"), row.names = FALSE)
write.csv(bob_posthoc$all, file.path(OUTPUT_DIR,"perm_posthoc_bob.csv"), row.names = FALSE)
write.csv(oh_posthoc$all,  file.path(OUTPUT_DIR,"perm_posthoc_oh.csv"),  row.names = FALSE)
```


## Load perm results 
```{r}
# --- Load saved results (no permutations run) ---
# Omnibus F-tests
apm_permutation_results <- read.csv(file.path(OUTPUT_DIR,"perm_F_results_apm.csv"), check.names = FALSE)
vgr_permutation_results <- read.csv(file.path(OUTPUT_DIR,"perm_F_results_vgr.csv"), check.names = FALSE)
bob_permutation_results <- read.csv(file.path(OUTPUT_DIR,"perm_F_results_bob.csv"), check.names = FALSE)
oh_permutation_results  <- read.csv(file.path(OUTPUT_DIR,"perm_F_results_oh.csv"),  check.names = FALSE)

# Posthoc results (wrap into the same structure your plotting fn expects)
apm_posthoc <- list(all = read.csv(file.path(OUTPUT_DIR,"perm_posthoc_apm.csv"), check.names = FALSE))
#vgr_posthoc <- list(all = read.csv(file.path(OUTPUT_DIR,"perm_posthoc_vgr.csv"), check.names = FALSE))
bob_posthoc <- list(all = read.csv(file.path(OUTPUT_DIR,"perm_posthoc_bob.csv"), check.names = FALSE))
#oh_posthoc  <- list(all = read.csv(file.path(OUTPUT_DIR,"perm_posthoc_oh.csv"),  check.names = FALSE))

# (Optional but helpful) ensure character columns are characters, not factors
for (dfn in c("apm_permutation_results","vgr_permutation_results",
              "bob_permutation_results","oh_permutation_results")) {
  tmp <- get(dfn)
  char_like <- c("parameter","significance","subjects_removed")
  for (cc in intersect(char_like, names(tmp))) tmp[[cc]] <- as.character(tmp[[cc]])
  assign(dfn, tmp)
}
for (lst in c("apm_posthoc","bob_posthoc")) {
  tmp <- get(lst)$all
  char_like <- c("parameter","comparison","significance","subjects_removed")
  for (cc in intersect(char_like, names(tmp))) tmp[[cc]] <- as.character(tmp[[cc]])
  assign(lst, list(all = tmp))
}

```


# Plots 

```{r, fig.width=5, fig.height=6}
# Load required libraries
library(ggplot2)
library(dplyr)

plot_behavioral_parameter_with_stats <- function(data, parameter, perm_results = NULL, 
                                                posthoc_results = NULL, save_plot = TRUE, 
                                                output_dir = PLOTS_OUTPUT_DIR, 
                                                width = 5, height = 7, dpi = 400) {
  
  # Create output directory if it doesn't exist
  if (save_plot && !dir.exists(output_dir)) {
    dir.create(output_dir, recursive = TRUE)
  }
  
  # Define colors for stimulation conditions (mapped to clean labels)
  condition_colors <- c("Unilateral" = "#e3d54a", "Bilateral" = "#da4f33", "Sham" = "#66a6ba")
  
  # Prepare data for plotting
  plot_data <- data %>%
    dplyr::select(subject, stimulation_condition, all_of(parameter)) %>%
    dplyr::filter(!is.na(.data[[parameter]])) %>%  # Only remove missing values
    dplyr::mutate(
      stimulation_condition = factor(stimulation_condition, 
                                   levels = c("sham", "ua-tDCS", "bi-tDCS"),
                                   labels = c("Sham", "Unilateral", "Bilateral"))
    )
  
  # Check if data exists for the parameter
  if (nrow(plot_data) == 0) {
    warning(paste("No data available for parameter:", parameter))
    return(NULL)
  }
  
  # Create clean parameter name for title
  param_title <- gsub("_", " ", parameter)
  param_title <- tools::toTitleCase(param_title)
  
  cat(paste0("Parameter: ", parameter, "\n"))
  cat(paste0("Number of observations: ", nrow(plot_data), "\n"))
  cat(paste0("Number of subjects: ", dplyr::n_distinct(plot_data$subject), "\n\n"))
  
  # Create the base plot
  p <- ggplot(plot_data, aes(x = stimulation_condition, y = .data[[parameter]])) +
    geom_boxplot(aes(fill = stimulation_condition), alpha = 0.7, outlier.shape = NA, width = 0.6) +
    geom_point(
      aes(fill = stimulation_condition),
      position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
      shape = 21,
      size = 3,
      alpha = 0.8,
      stroke = 1.5,
      color = "black",
      show.legend = FALSE
    ) +
    scale_fill_manual(values = condition_colors) +
    labs(
      title = "",
      x = "",
      y = "",
      fill = "Condition"
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",
      plot.title = element_text(face = "bold", size = 20),
      plot.subtitle = element_text(size = 20),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 18),
      legend.title = element_text(face = "bold", size = 18),
      axis.title.y = element_text(margin = margin(r = 15)),
      legend.text = element_text(size = 16),    
      strip.text = element_text(face = "bold", size = 18), 
      panel.grid.major.x = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),
      plot.background = element_rect(fill = "white", color = NA),
      axis.line = element_line(color = "black", size = 0.5),
      panel.border = element_blank()
    )
  
  if (save_plot) {
    filename <- file.path(output_dir, paste0(parameter, "_boxplot.png"))
    ggsave(filename, plot = p, width = width, height = height, dpi = dpi, bg = "white")
    cat("Plot saved as:", filename, "\n\n")
  }
  
  print(p)
  return(p)
}
```



```{r, fig.width=5, fig.height=7, fig.dpi=400}
# APM parameter: LH_variability_x_m
LH_variability_x_m_plot <- plot_behavioral_parameter_with_stats(apm_wide, "LH_variability_x_m", 
                                    perm_results = apm_permutation_results,
                                    posthoc_results = apm_posthoc)

# BOB parameter: x2_bar_length_variability  
x2_bar_length_variability_plot <- plot_behavioral_parameter_with_stats(bob_data, "x2_bar_length_variability", 
                                    perm_results = bob_permutation_results,
                                    posthoc_results = bob_posthoc)
```



# Learnig effects (NONE)

```{r}
# ============================================================================
# LEARNING EFFECT ANALYSIS (Session Number)
# ============================================================================

## Learning effect analysis function (corrected)
analyze_learning_effect <- function(data, param_list, print_progress = TRUE) {
  # Fixed columns
  subject_col <- "subject"
  session_col <- "session_no"
  
  # Ensure session_no is ordered factor
  if (!session_col %in% names(data)) {
    stop(paste("Column", session_col, "not found in data"))
  }
  
  data[[session_col]] <- ordered(data[[session_col]], levels = c(1, 2, 3))
  
  results_df <- data.frame(
    parameter = character(),
    f_statistic = numeric(),
    df_num = numeric(),
    df_denom = numeric(),
    p_value = numeric(),
    n_obs = integer(),
    n_subjects = integer(),
    singular_fit = logical(),
    significance = character(),
    stringsAsFactors = FALSE
  )
  
  for (param in param_list) {
    if (print_progress) {
      cat("##########################\n")
      cat("Learning Effect Analysis for:", param, "\n")
    }
    
    # Formula: y ~ session_no + (1|subject)
    formula <- as.formula(sprintf("%s ~ %s + (1|%s)", param, session_col, subject_col))
    if (print_progress) cat("Formula:", deparse(formula), "\n")
    
    # Select data for this parameter (no outlier removal)
    model_df <- data %>%
      dplyr::select(dplyr::all_of(c(subject_col, session_col, param))) %>%
      dplyr::filter(!is.na(.data[[param]]))
    
    n_obs <- nrow(model_df)
    n_subjects <- dplyr::n_distinct(model_df[[subject_col]])
    
    if (print_progress) {
      cat("Total observations:", n_obs, "\n")
      cat("Number of subjects:", n_subjects, "\n")
    }
    
    # Check if enough data
    if (n_obs == 0 || n_subjects < 2) {
      if (print_progress) cat("Not enough data. Skipping", param, "\n\n")
      results_df <- rbind(
        results_df,
        data.frame(
          parameter = param,
          f_statistic = NA_real_,
          df_num = NA_real_,
          df_denom = NA_real_,
          p_value = NA_real_,
          n_obs = n_obs,
          n_subjects = n_subjects,
          singular_fit = NA,
          significance = "ns",
          stringsAsFactors = FALSE
        )
      )
      next
    }
    
    # Fit model and check for singularity
    singular_fit <- FALSE
    model_fit <- tryCatch({
      withCallingHandlers(
        lme4::lmer(formula, data = model_df, REML = FALSE),
        warning = function(w) {
          if (grepl("singular", w$message, ignore.case = TRUE)) {
            singular_fit <<- TRUE
          }
        }
      )
    }, error = function(e) {
      if (print_progress) cat("Error fitting model:", e$message, "\n\n")
      return(NULL)
    })
    
    if (is.null(model_fit)) {
      results_df <- rbind(
        results_df,
        data.frame(
          parameter = param,
          f_statistic = NA_real_,
          df_num = NA_real_,
          df_denom = NA_real_,
          p_value = NA_real_,
          n_obs = n_obs,
          n_subjects = n_subjects,
          singular_fit = NA,
          significance = "ns",
          stringsAsFactors = FALSE
        )
      )
      next
    }
    
    # Get ANOVA results using lmerTest
    anova_result <- tryCatch({
      anova(model_fit)
    }, error = function(e) {
      if (print_progress) cat("Error in ANOVA:", e$message, "\n\n")
      return(NULL)
    })
    
    if (is.null(anova_result)) {
      results_df <- rbind(
        results_df,
        data.frame(
          parameter = param,
          f_statistic = NA_real_,
          df_num = NA_real_,
          df_denom = NA_real_,
          p_value = NA_real_,
          n_obs = n_obs,
          n_subjects = n_subjects,
          singular_fit = singular_fit,
          significance = "ns",
          stringsAsFactors = FALSE
        )
      )
      next
    }
    
    # Extract statistics safely
    f_stat <- if("F value" %in% names(anova_result)) anova_result$`F value`[1] else NA_real_
    p_val <- if("Pr(>F)" %in% names(anova_result)) anova_result$`Pr(>F)`[1] else NA_real_
    df_num <- if("NumDF" %in% names(anova_result)) anova_result$NumDF[1] else 
              if("npar" %in% names(anova_result)) anova_result$npar[1] else NA_real_
    df_denom <- if("DenDF" %in% names(anova_result)) anova_result$DenDF[1] else NA_real_
    
    sig_level <- ifelse(is.na(p_val), "ns",
                 ifelse(p_val < 0.001, "***",
                 ifelse(p_val < 0.01,  "**",
                 ifelse(p_val < 0.05,  "*", "ns"))))
    
    results_df <- rbind(
      results_df,
      data.frame(
        parameter = param,
        f_statistic = f_stat,
        df_num = df_num,
        df_denom = df_denom,
        p_value = p_val,
        n_obs = n_obs,
        n_subjects = n_subjects,
        singular_fit = singular_fit,
        significance = sig_level,
        stringsAsFactors = FALSE
      )
    )
    
    if (print_progress) {
      cat("Singular fit:", singular_fit, "\n")
      cat("F-statistic:", f_stat, "\n")
      cat("df:", df_num, ",", df_denom, "\n")
      cat("p-value:", p_val, "\n")
      cat("Significance:", sig_level, "\n\n")
    }
  }
  
  results_df
}
```


```{r}
# ============================================================================
# RUN LEARNING EFFECT ANALYSIS FOR ALL TASKS AND SAVE RESULTS
# ============================================================================

## Run learning effect analysis for all tasks

cat("\n============================================================\n")
cat("LEARNING EFFECT ANALYSIS: APM\n")
cat("============================================================\n")
apm_learning_results <- analyze_learning_effect(
  data = apm_wide,
  param_list = apm_behavior_vars_both_hands,
  print_progress = FALSE
)

cat("\n============================================================\n")
cat("LEARNING EFFECT ANALYSIS: VGR\n")
cat("============================================================\n")
vgr_learning_results <- analyze_learning_effect(
  data = vgr_wide,
  param_list = vgr_behavior_vars_both_hands,
  print_progress = FALSE
)

cat("\n============================================================\n")
cat("LEARNING EFFECT ANALYSIS: BOB\n")
cat("============================================================\n")
bob_learning_results <- analyze_learning_effect(
  data = bob_data,
  param_list = bob_behavior_vars,
  print_progress = FALSE
)

cat("\n============================================================\n")
cat("LEARNING EFFECT ANALYSIS: OH\n")
cat("============================================================\n")
oh_learning_results <- analyze_learning_effect(
  data = oh_data,
  param_list = oh_behavior_vars,
  print_progress = FALSE
)

## Combine all learning effect results
all_learning_results <- rbind(
  apm_learning_results %>% mutate(task = "APM"),
  vgr_learning_results %>% mutate(task = "VGR"),
  bob_learning_results %>% mutate(task = "BOB"),
  oh_learning_results %>% mutate(task = "OH")
)

## Display significant results only
cat("\n============================================================\n")
cat("PARAMETERS SHOWING LEARNING EFFECTS (p < 0.05)\n")
cat("============================================================\n")

sig_results <- all_learning_results %>% 
  filter(significance %in% c("*", "**", "***")) %>%
  arrange(task, p_value) %>%
  select(task, parameter, f_statistic, p_value, n_obs, significance)

if (nrow(sig_results) > 0) {
  print(sig_results, digits = 4)
  cat("\nTotal significant learning effects:", nrow(sig_results), "\n")
} else {
  cat("\nNo significant learning effects found.\n")
}

## Save results
write.csv(all_learning_results, 
          file.path(OUTPUT_DIR, "learning_effect_all_tasks.csv"), 
          row.names = FALSE)
```




