---
title: "Statistical analysis CAPs dynamics.Rmd"
output:
  pdf_document: default
  html_document: default
date: "2025-06-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(results="asis")
knitr::opts_chunk$set(warning = FALSE)
```

This notebook tests whether tDCS (sham, unilateral, bilateral) affects CAPs dynamics measures (occurrence rate, dwell time, transition probability) across subjects.

1.  **Omnibus test**: within-subject permutation LMER F-test (`param ~ session + (1|subject)`) for each CAP, with condition labels shuffled within each subject.
2.  **Post-hoc**: paired permutation t-tests for the three pairwise comparisons (unilateral vs sham, bilateral vs sham, bilateral vs unilateral), with Bonferroni correction applied within each parameter across the three comparisons.

```{r}
library(lme4)
library(lmerTest)
library(dplyr)
library(knitr)
library(emmeans)
library(knitr)
library(ggpubr)
library(rstatix)
library(sjPlot)
library(sjtable2df)
library(report)
library(ggplot2)
library(dplyr)
library(tidyr)
library(performance)
#library(flexplot)
library(DHARMa)
library(gt)
```

```{r}
prepare_df <- function(file_path) {
  # Read data from the provided file path
  data <- read.csv(file_path)
  
  # Clean up columns: remove original session/run and rename _name columns
  data <- data %>%
    select(-session, -run) %>%
    rename(session = session_name, run = run_name)
  
  # Filter to include only "On" data
  data_on <- data    #%>% filter(run == "tDCS On")
  
  # Convert factors with proper reference levels
  data_on$session <- factor(data_on$session, levels = c("Sham", "Unilateral", "Bilateral"))
  data_on$subject <- factor(data_on$subject)
  return(data_on)
}
```

# LMER permutation F-tets

## Perm F-test functions

```{r}
get_perm_f_val_caps <- function(data, param_list, n_perm = 10000,
                                 print_progress = TRUE, seed = 123) {
  # Fixed columns / reference
  subject_col <- "subject"
  condition_col <- "session"
  ref_level <- "Sham"

  # Store base seed for parameter-specific seeding
  base_seed <- seed

  # Ensure factor with reference level
  data[[condition_col]] <- relevel(as.factor(data[[condition_col]]), ref = ref_level)

  results_df <- data.frame(
    parameter = character(),
    f_statistic = numeric(),
    df_num = numeric(),
    df_denom = numeric(),
    p_value = numeric(),
    n_valid_perms = integer(),
    n_obs = integer(),
    singular_warnings = integer(),
    original_singular = logical(),
    significance = character(),
    stringsAsFactors = FALSE
  )

  for (i in seq_along(param_list)) {
    param <- param_list[i]
    
    # Set parameter-specific seed for reproducibility
    if (!is.null(base_seed)) {
      set.seed(base_seed + i - 1)
    }
    
    if (print_progress) {
      cat("##########################\n")
      cat("Within-Subject Permutation Test for:", param, "\n")
      if (!is.null(base_seed)) {
        cat("Seed:", base_seed + i - 1, "\n")
      }
    }

    # formula y ~ condition + (1|subject)
    formula <- as.formula(sprintf("%s ~ %s + (1|%s)", param, condition_col, subject_col))
    if (print_progress) cat("Formula:", deparse(formula), "\n")

    # Select data for this parameter (NO outlier removal)
    model_df <- data %>%
      dplyr::select(dplyr::all_of(c(subject_col, condition_col, param))) %>%
      dplyr::filter(!is.na(.data[[param]]))  # Only remove missing values

    n_obs <- nrow(model_df)
    n_subjects <- dplyr::n_distinct(model_df[[subject_col]])

    if (print_progress) {
      cat("Total observations:", n_obs, "\n")
      cat("Number of subjects:", n_subjects, "\n")
    }

    # Check if enough data
    if (n_obs == 0 || n_subjects < 2) {
      if (print_progress) cat("Not enough data. Skipping", param, "\n\n")
      results_df <- rbind(
        results_df,
        data.frame(
          parameter = param,
          f_statistic = NA_real_,
          df_num = NA_real_,
          df_denom = NA_real_,
          p_value = NA_real_,
          n_valid_perms = 0L,
          n_obs = n_obs,
          singular_warnings = NA_integer_,
          original_singular = NA,
          significance = "ns",
          stringsAsFactors = FALSE
        )
      )
      next
    }

    # Call permutation (uses current RNG state from set.seed above)
    perm_result <- permutation_test_lmer(
      formula = formula,
      data = model_df,
      group_var = condition_col,
      subject_col = subject_col,
      n_perm = n_perm
    )

    sig_level <- ifelse(perm_result$p_value < 0.001, "***",
                 ifelse(perm_result$p_value < 0.01,  "**",
                 ifelse(perm_result$p_value < 0.05,  "*", "ns")))

    results_df <- rbind(
      results_df,
      data.frame(
        parameter = param,
        f_statistic = perm_result$original_f,
        df_num = perm_result$df_num,
        df_denom = perm_result$df_denom,
        p_value = perm_result$p_value,
        n_valid_perms = perm_result$n_valid_perms,
        n_obs = n_obs,
        singular_warnings = perm_result$singular_warnings,
        original_singular = perm_result$original_singular,
        significance = sig_level,
        stringsAsFactors = FALSE
      )
    )

    if (print_progress) {
      cat("\n")
      cat("Original model singular:", perm_result$original_singular, "\n")
      cat("Singular warnings in permutations:", perm_result$singular_warnings, "out of", n_perm, "\n")
      cat("Original F-statistic:", perm_result$original_f, "\n")
      cat("Permutation p-value:", perm_result$p_value, "\n")
      cat("Valid permutations:", perm_result$n_valid_perms, "out of", n_perm, "\n")
      cat("Significance:", sig_level, "\n\n")
    }
  }

  results_df
}

permutation_test_lmer <- function(formula, data, group_var, subject_col, n_perm = 10000) {
  # Fit original model and capture singularity warning
  original_singular <- FALSE
  original_model <- tryCatch({
    withCallingHandlers(
      lme4::lmer(formula, data = data, REML = FALSE),
      warning = function(w) {
        if (grepl("singular", w$message, ignore.case = TRUE)) {
          original_singular <<- TRUE
        }
      }
    )
  }, error = function(e) {
    stop("Error fitting original model: ", e$message)
  })

  anova_tbl      <- anova(original_model)
  original_fstat <- anova_tbl$`F value`[1]
  # df_num: always k-1 conditions (robust to anova table column name differences)
  df_num         <- nlevels(data[[group_var]]) - 1L
  # df_denom: Satterthwaite via lmerTest (convert without refitting)
  lt_anova       <- tryCatch(
    anova(lmerTest::as_lmerModLmerTest(original_model)),
    error = function(e) NULL
  )
  df_denom       <- if (!is.null(lt_anova) && "DenDF" %in% names(lt_anova)) lt_anova$DenDF[1] else NA_real_

  # Permutation test: shuffle group labels WITHIN each subject
  perm_fstats <- numeric(n_perm)
  singular_count <- 0L

  for (i in seq_len(n_perm)) {
    perm_data <- data %>%
      dplyr::group_by(!!dplyr::sym(subject_col)) %>%
      dplyr::mutate(
        !!dplyr::sym(group_var) := sample(.data[[group_var]])
      ) %>%
      dplyr::ungroup()

    # Fit permuted model and record F (handle singular fits/warnings)
    tryCatch({
      withCallingHandlers(
        {
          perm_model <- lme4::lmer(formula, data = perm_data, REML = FALSE)
          perm_fstats[i] <- anova(perm_model)$`F value`[1]
        },
        warning = function(w) {
          if (grepl("singular", w$message, ignore.case = TRUE)) {
            singular_count <<- singular_count + 1L
          }
        }
      )
    }, error = function(e) {
      perm_fstats[i] <- NA_real_
    })
  }

  # Remove NAs and compute p-value (right-tail, as F is larger = more extreme)
  perm_fstats <- perm_fstats[!is.na(perm_fstats)]
  p_value <- mean(perm_fstats >= original_fstat, na.rm = TRUE)

  list(
    original_f = original_fstat,
    df_num = df_num,
    df_denom = df_denom,
    p_value = p_value,
    n_valid_perms = length(perm_fstats),
    singular_warnings = singular_count,
    original_singular = original_singular
  )
}
```

## Global params

Global number of permutations and dirs

```{r}
library(dotenv)
load_dot_env(file = "../.env")

N_PERM = 10000

BASE_DIR    <- Sys.getenv("BASE_DIR")
RESULTS_DIR <- Sys.getenv("RESULTS_DIR")

INPUT_DIR <- file.path(BASE_DIR)
OUTPUT_DIR <- file.path(RESULTS_DIR, "stats", "02_caps")
PLOTS_OUTPUT_DIR <- file.path(RESULTS_DIR, "main_figures", "05_caps_stats")

dir.create(OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
dir.create(PLOTS_OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
```

## Occurence rate

```{r}
k=7
occ_data <- prepare_df(file.path(INPUT_DIR, "caps_dynamics_run-ON", 
                                 paste0("caps_nclust-", k), "CAP_occurence_times.csv"))
str(occ_data)
head(occ_data)
```

```{r}
cap_var_names <- c("CAP1", "CAP2", "CAP3", "CAP4", "CAP5", "CAP6", "CAP7")
occ_permutation_results <- get_perm_f_val_caps(
  data = occ_data,
  param_list = cap_var_names,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(occ_permutation_results)
```

## Dwell time

```{r}
k=7
dt_data <- prepare_df(file.path(INPUT_DIR, "caps_dynamics_run-ON", 
                                paste0("caps_nclust-", k), "CAP_dwelltime.csv"))
str(dt_data)
head(dt_data)
```

```{r}
cap_var_names <- c("CAP1", "CAP2", "CAP3", "CAP4", "CAP5", "CAP6", "CAP7")
dt_permutation_results <- get_perm_f_val_caps(
  data = dt_data,
  param_list = cap_var_names,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(dt_permutation_results)
```

## Transition probability

```{r}
tp_data <- prepare_df(file.path(INPUT_DIR, "caps_dynamics_run-ON", 
                                paste0("caps_nclust-", k), "CAP_transitions_full.csv"))
str(tp_data)
head(tp_data)
```

```{r}
tp_wide <- tp_data %>%
  mutate(CAP_pair = paste0(from_CAP, "_", to_CAP)) %>%
  pivot_wider(
    id_cols = c(data_label, subject, session, run),  # keep these as identifiers
    names_from = CAP_pair,
    values_from = c(transition_probability),  # pivot both measures
    values_fill = 0   # fill missing with 0
  )
str(tp_wide)
head(tp_wide)
cap_tp_cols <- grep("^CAP[0-9]+_CAP[0-9]+$", names(tp_wide), value = TRUE)
cap_tp_cols
```

```{r, warning=FALSE, message=FALSE, results='hide'}
#cap_tp_cols = c("CAP1_CAP7", "CAP6_CAP1")
tp_permutation_results <- get_perm_f_val_caps(
  data = tp_wide,
  param_list = cap_tp_cols,
  n_perm = N_PERM,
  print_progress = TRUE
)
print(tp_permutation_results)
```

## Save F permutation results

```{r}
# --- Omnibus permutation F-test results ---
write.csv(occ_permutation_results,
          file.path(OUTPUT_DIR, "perm_F_results_occ.csv"), row.names = FALSE)
write.csv(dt_permutation_results,
          file.path(OUTPUT_DIR, "perm_F_results_dt.csv"), row.names = FALSE)
write.csv(tp_permutation_results,
          file.path(OUTPUT_DIR, "perm_F_results_tp.csv"), row.names = FALSE)
```

# Post-hoc permutation t-tests

## Perm pair-wise t-tests function

```{r}
library(MKinfer)
# Function to perform pairwise permutation t-tests with correction
perform_pairwise_tests <- function(
  caps_df,
  cap_params,
  n_perm = 10000,
  correction_method = "bonferroni"
) {
  # NO seeding here - relies on parent function setting RNG state
  
  subject_col <- "subject"
  condition_col <- "session"

  # Comparisons (order matters for reporting)
  comparisons <- list(
    c("Unilateral", "Sham"),
    c("Bilateral", "Sham"),
    c("Bilateral", "Unilateral")
  )

  # Container for all parameters
  results_df <- data.frame(
    parameter = character(),
    comparison = character(),
    n_pairs = integer(),
    df = integer(),
    statistic = numeric(),
    p_value = numeric(),
    p_corrected = numeric(),
    cohens_d = numeric(),
    significance = character(),
    stringsAsFactors = FALSE
  )

  for (param in cap_params) {

    # Collect this parameter's three pairwise tests
    param_results <- data.frame(
      parameter = character(),
      comparison = character(),
      n_pairs = integer(),
      df = integer(),
      statistic = numeric(),
      p_value = numeric(),
      cohens_d = numeric(),
      stringsAsFactors = FALSE
    )

    for (comp in comparisons) {
      cond1 <- comp[1]
      cond2 <- comp[2]

      # 1) Subset to the two conditions + subject + current param
      sub_df <- caps_df[caps_df[[condition_col]] %in% c(cond1, cond2),
                        c(subject_col, condition_col, param)]
      names(sub_df) <- c(subject_col, condition_col, "y")

      # 2) Wide by condition to align pairs by subject
      wide <- tidyr::pivot_wider(
        sub_df,
        id_cols = tidyselect::all_of(subject_col),
        names_from = tidyselect::all_of(condition_col),
        values_from = "y"
      )

      # Keep only rows where both conditions are present (paired)
      if (!all(c(cond1, cond2) %in% names(wide))) {
        data1 <- numeric(0)
        data2 <- numeric(0)
      } else {
        wide <- wide[stats::complete.cases(wide[, c(cond1, cond2), drop = FALSE]), , drop = FALSE]
        data1 <- wide[[cond1]]
        data2 <- wide[[cond2]]
      }

      # If too few pairs, store NA row
      if (length(data1) < 2L) {
        param_results <- rbind(param_results,
          data.frame(
            parameter = param,
            comparison = paste(cond1, "vs", cond2),
            n_pairs = length(data1),
            df = NA_integer_,
            statistic = NA_real_,
            p_value = NA_real_,
            cohens_d = NA_real_,
            stringsAsFactors = FALSE
          )
        )
        next
      }

      # 3) Permutation paired t-test (uses current RNG state)
      perm_test <- MKinfer::perm.t.test(data1, data2, paired = TRUE, R = n_perm)

      # 4) Cohen's d for paired data
      dvals <- data1 - data2
      cohens_d_val <- mean(dvals, na.rm = TRUE) / stats::sd(dvals, na.rm = TRUE)

      # 5) Collect results
      param_results <- rbind(param_results,
        data.frame(
          parameter = param,
          comparison = paste(cond1, "vs", cond2),
          n_pairs = length(dvals),
          df = length(dvals) - 1L,
          statistic = unname(perm_test$statistic),
          p_value = unname(perm_test$p.value),
          cohens_d = cohens_d_val,
          stringsAsFactors = FALSE
        )
      )
    }

    # 6) Multiple-comparison correction within this parameter (across its 3 tests)
    param_results$p_corrected <- stats::p.adjust(param_results$p_value, method = correction_method)

    # 7) Significance marks
    param_results$significance <- ifelse(!is.na(param_results$p_corrected) & param_results$p_corrected < 0.05, "**",
                                  ifelse(!is.na(param_results$p_value)     & param_results$p_value     < 0.05, "*",
                                  ifelse(!is.na(param_results$p_value)     & param_results$p_value     < 0.10, ".", "")))

    # 8) Append to all results
    results_df <- rbind(results_df,
                        param_results[, c("parameter","comparison","n_pairs","df","statistic","p_value","p_corrected","cohens_d","significance")])
  }

  # Significant-only view
  sig_results <- subset(results_df, significance %in% c(".", "*", "**"))

  list(
    all_results = results_df,
    significant_results = sig_results
  )
}


# Post-hoc permutation t-tests for significant F-tests
run_posthoc_permutation <- function(
  f_results_df,
  caps_df,
  alpha = 0.05,
  n_perm = 10000,
  seed = 123,
  correction_method = "bonferroni"
) {
  
  base_seed <- seed
  subject_col   <- "subject"
  condition_col <- "session"

  # Which parameters are significant at the omnibus level
  sig_params <- f_results_df$parameter[f_results_df$p_value < alpha] 
  
  if (length(sig_params) == 0L) {
    message("No parameters passed the F-test threshold; nothing to run post-hoc on.")
    return(list(all = data.frame(), by_param = list()))
  }

  all_posthoc <- list()

  for (i in seq_along(sig_params)) {
    param <- sig_params[i]
    
    # Set seed ONCE for this parameter (covers all 3 comparisons)
    if (!is.null(base_seed)) {
      set.seed(base_seed + i - 1)
    }
    
    # Use all data (NO outlier removal)
    filtered_df <- caps_df

    # Run the paired permutation post-hoc comparisons for THIS param only
    ph <- perform_pairwise_tests(
      caps_df = filtered_df,
      cap_params = param, 
      n_perm = n_perm,
      correction_method = correction_method
    )

    all_posthoc[[param]] <- ph$all_results
  }

  combined <- do.call(rbind, all_posthoc)

  # Return both a combined df and split-by-parameter list
  list(
    all = combined[order(combined$parameter, combined$comparison), ],
    by_param = all_posthoc
  )
}
# Small helper for null-coalescing (replace NULL/NA with "")
`%||%` <- function(a, b) {
  if (is.null(a) || (length(a) == 1 && is.na(a))) b else a
}

```

## Occurence rate

```{r}
occ_posthoc <- run_posthoc_permutation(
  f_results_df = occ_permutation_results,
  caps_df = occ_data,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "bonferroni"  
)
occ_posthoc$all
```

## Dwell time

```{r}
dt_posthoc <- run_posthoc_permutation(
  f_results_df = dt_permutation_results,
  caps_df = dt_data,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "bonferroni"  
)
dt_posthoc$all
```

## Transition Probability

```{r}
tp_permutation_results_clean <- tp_permutation_results %>%
  filter(!is.nan(f_statistic))
head(tp_permutation_results_clean)
str(tp_permutation_results_clean)
```

```{r}
tp_posthoc <- run_posthoc_permutation(
  f_results_df = tp_permutation_results_clean,
  caps_df = tp_wide,
  alpha = 0.05,
  n_perm = N_PERM,
  seed = 123,     
  correction_method = "bonferroni"  
)
tp_posthoc$all
```

## Save post-hoc permutation results

```{r}
# --- Post-hoc permutation t-test results ---
write.csv(occ_posthoc$all,
          file.path(OUTPUT_DIR, "perm_posthoc_occ.csv"), row.names = FALSE)
write.csv(dt_posthoc$all,
          file.path(OUTPUT_DIR, "perm_posthoc_dt.csv"), row.names = FALSE)
write.csv(tp_posthoc$all,
          file.path(OUTPUT_DIR, "perm_posthoc_tp.csv"), row.names = FALSE)

# --- Metadata for reproducibility ---
meta <- data.frame(
  k = 7,
  N_PERM = N_PERM,
  timestamp = format(Sys.time(), "%Y-%m-%d %H:%M:%S"),
  stringsAsFactors = FALSE
)
write.csv(meta, file.path(OUTPUT_DIR, "run_metadata.csv"), row.names = FALSE)
```

## Read saved reults

```{r}
safe_read_csv <- function(path) {
  tryCatch(
    read.csv(path),
    error = function(e) {
      message("Could not read ", basename(path), " — returning empty dataframe")
      data.frame()
    }
  )
}

occ_permutation_results <- safe_read_csv(file.path(OUTPUT_DIR, "perm_F_results_occ.csv"))
dt_permutation_results  <- safe_read_csv(file.path(OUTPUT_DIR, "perm_F_results_dt.csv"))
tp_permutation_results <- safe_read_csv(file.path(OUTPUT_DIR, "perm_F_results_tp.csv"))

occ_posthoc_all <- safe_read_csv(file.path(OUTPUT_DIR, "perm_posthoc_occ.csv"))
dt_posthoc_all  <- safe_read_csv(file.path(OUTPUT_DIR, "perm_posthoc_dt.csv"))
tp_posthoc_all  <- safe_read_csv(file.path(OUTPUT_DIR, "perm_posthoc_tp.csv"))

```

# Plot OCC and DT

```{r}
################################################################################
####### Create box plots and bar plots of occurrence rate and dwell time #######
################################################################################

library(lme4)
library(lmerTest)
library(dplyr)
library(knitr)
library(emmeans)
library(knitr)
library(ggpubr)
library(rstatix)
library(lme4)
library(lmerTest)
library(dplyr)
library(knitr)
library(emmeans)
library(knitr)
library(ggpubr)
library(rstatix)
library(sjPlot)
library(sjtable2df)
library(report)
library(ggplot2)
library(dplyr)
library(tidyr)
library(performance)
library(gridExtra)
library(grid)
library(patchwork)

 

prepare_df_only_on <- function(file_path) {
  # Read data from the provided file path
  data <- read.csv(file_path)
  
  # Clean up columns: remove original session/run and rename _name columns
  data <- data %>%
    select(-session, -run) %>%
    rename(session = session_name, run = run_name)
  
  # Filter to include only "On" data
  data_on <- data %>% filter(run == "tDCS On")
  
  # Convert factors with proper reference levels
  data_on$session <- factor(data_on$session, levels = c("Sham", "Unilateral", "Bilateral"))
  data_on$subject <- factor(data_on$subject)
  return(data_on)
}

plot_cap_stats_only_on <- function(data_on, k, data_type, data_type_out_str) {
  cap_cols <- grep("^CAP\\d+$", colnames(data_on), value = TRUE)
  data_on$session <- factor(data_on$session, levels = c("Unilateral", "Bilateral", "Sham"))
  
  if (length(cap_cols) == 0) {
    stop("No columns with the pattern 'CAPn' found in the data")
  }
  
  # Convert data to long format for easier plotting
  data_long <- data_on %>%
    pivot_longer(
      cols = all_of(cap_cols),
      names_to = "CAP",
      values_to = "value"
    )
  
  # Calculate mean and SD by CAP and session
  stats_by_group <- data_long %>%
    group_by(CAP, session) %>%
    summarize(
      mean_value = mean(value, na.rm = TRUE),
      sd_value = sd(value, na.rm = TRUE),
      se_value = sd_value / sqrt(n()),
      n = n(),
      .groups = "drop"
    )
  
  # Create a plot of means with error bars (using SE instead of SD)
  p1 <- ggplot(stats_by_group, aes(x = CAP, y = mean_value, fill = session)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7, alpha = 0.8) +
    geom_errorbar(
      aes(ymin = mean_value - se_value, ymax = mean_value + se_value),
      position = position_dodge(width = 0.8),
      width = 0.25
    ) +
    scale_fill_manual(values = c("Unilateral" = "#e3d54a", "Bilateral" = "#da4f33", "Sham" = "#66a6ba")) +
    labs(
      title = "",
      subtitle = "Error bars represent standard error",
      x = "",
      y = paste("\n\n", data_type),
      fill = "Session"
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",  # Remove legend from plot
      plot.title = element_text(face = "bold", size=20),
      plot.subtitle = element_text(size=20),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 18),
      legend.title = element_text(face = "bold", size = 18),
      axis.title.y = element_text(margin = margin(r = 15)),
      legend.text = element_text(size = 16),    
      strip.text = element_text(face = "bold", size = 18), 
      panel.grid.major.x = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),
      plot.background = element_rect(fill = "white", color = NA),
      # Add axis frames
      axis.line = element_line(color = "black", size = 0.5),
      panel.border = element_blank()
    )
  
  # Save individual plots
  ggsave(file.path(PLOTS_OUTPUT_DIR, paste0("mean_se_", data_type_out_str, ".png")), 
         p1, width = 9, height = 4, dpi = 400)
  
  # Create boxplot with data points
  p2 <- ggplot(data_long, aes(x = CAP, y = value, fill = session)) +
    geom_boxplot(position = position_dodge(width = 0.8,), 
                 width = 0.7, 
                 alpha = 0.7) +
    scale_fill_manual(values = c("Unilateral" = "#e3d54a", "Bilateral" = "#da4f33", "Sham" = "#66a6ba")) +
    geom_point(
      aes(fill = session),
      position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
      shape = 21,
      size = 1.5,
      alpha = 0.6,
      stroke = 0.5,
      color = "black",
      show.legend = FALSE
    ) +
    labs(
      title = "",
      x = "",
      y = paste("\n\n", data_type),
      fill = "Session"
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",  # Remove legend from plot
      plot.title = element_text(face = "bold", size=20),
      plot.subtitle = element_text(size=20),
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 18),
      legend.title = element_text(face = "bold", size = 18),
      axis.title.y = element_text(margin = margin(r = 15)),
      legend.text = element_text(size = 16),    
      strip.text = element_text(face = "bold", size = 18), 
      panel.grid.major.x = element_blank(),
      panel.background = element_rect(fill = "white", color = NA),
      plot.background = element_rect(fill = "white", color = NA),
      # Add axis frames
      axis.line = element_line(color = "black", size = 0.5),
      panel.border = element_blank()
    )
  
  ggsave(file.path(PLOTS_OUTPUT_DIR, paste0("R_box_plot_only_on_", data_type_out_str, ".png")), 
         p2, width = 9, height = 4, dpi = 400)
  
  # Create a simple plot just to generate the legend
  legend_data <- data.frame(
    x = rep(1, 3),
    y = rep(1, 3), 
    session = factor(c("Unilateral", "Bilateral", "Sham"), levels = c("Unilateral", "Bilateral", "Sham"))
  )
  
  legend_plot <- ggplot(legend_data, aes(x = x, y = y, fill = session)) +
    geom_col(width = 0.7, alpha = 0.8) +  # Use same geom as main plots
    scale_fill_manual(values = c("Unilateral" = "#e3d54a", "Bilateral" = "#da4f33", "Sham" = "#66a6ba")) +
    labs(fill = "") +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.title = element_text(face = "bold", size = 18),
      legend.text = element_text(size = 16),
      legend.margin = margin(0, 0, 0, 0),  # Remove legend margins
      legend.box.margin = margin(0, 0, 0, 0)  # Remove legend box margins
    )
  tmp <- ggplot_gtable(ggplot_build(legend_plot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend_only <- tmp$grobs[[leg]]
  
  # Save the legend as a separate plot in the same directory as box plots
  ggsave(file.path(PLOTS_OUTPUT_DIR, paste0("legend_", data_type_out_str, ".png")), 
         legend_only, width = 6, height = 1, dpi = 400, bg = "transparent")
  
  # Return the plot objects, legend, and stats data
  return(list(
    bar_plot = p1,
    box_plot = p2, 
    legend = legend_only,
    stats = stats_by_group
  ))
}

k=7
occ_results <- plot_cap_stats_only_on(occ_data, k=k, data_type="Occurrence Rate", data_type_out_str="occ_rate")
dt_results <- plot_cap_stats_only_on(dt_data, k=k, data_type="Dwell Time", data_type_out_str="dwell_time")

# Combine plots vertically with patchwork for perfect alignment
combined_plot <- occ_results$box_plot / dt_results$box_plot  
print(combined_plot)
ggsave(file.path(PLOTS_OUTPUT_DIR, "box_plot_combined_dwell_occurrence.png"), 
       combined_plot, width = 9, height = 8, dpi = 400)
```

## Correlation between DT and OCC

```{r}
corr_method <- "spearman"

df_occ_sham <- occ_data[occ_data$session == "Sham", ]
df_dt_sham  <- dt_data[dt_data$session == "Sham", ]
correlation <- cor.test(df_occ_sham$CAP4, df_dt_sham$CAP4, method = corr_method)

cat("Correlation in the sham stimulation------------------------------------\n")
correlation


df_occ_bi <- occ_data[occ_data$session == "Bilateral", ]
df_dt_bi  <- dt_data[dt_data$session == "Bilateral", ]
correlation <- cor.test(df_occ_bi$CAP4, df_dt_bi$CAP4, method = corr_method)

cat("Correlation in the Bilateral stimulation-------------------------------\n")
correlation


df_occ_uni <- occ_data[occ_data$session == "Unilateral", ]
df_dt_uni  <- dt_data[dt_data$session == "Unilateral", ]
correlation <- cor.test(df_occ_uni$CAP4, df_dt_uni$CAP4, method = corr_method)

cat("Correlation in the Unilateral stimulation------------------------------\n")
correlation
```
