---
title: "05 - Plot CAPs Transition Probabilities"
output: pdf_document
date: "2025-05-26"
---

This notebook analyses **CAP-to-CAP transition probabilities** for the tDCS study (Unilateral, Bilateral, Sham sessions, run-ON data, 7-CAP solution, N = 20 subjects).

It has two main sections:

1.  **Transition probability heatmaps** — mean transition probability matrices (from-CAP × to-CAP) are visualised for each session using an Oranges colour scale. Individual per-session heatmaps and a shared colourbar are saved to `main_figures/05_caps_tp`.

2.  **Cohen's d heatmaps** — paired Cohen's d (difference scores: session1 − session2, normalised by the SD of differences) is computed for each CAP pair across three pairwise session comparisons: Unilateral − Sham, Bilateral − Sham, and Bilateral − Unilateral. Results are plotted on a diverging blue–white–red scale (fixed ±0.6) and saved alongside a standalone colourbar. The full results table is saved to `stats/02_caps/cohens_d_transitions.csv`.

A final diagnostic section inspects the CAP7 → CAP6 transition specifically to understand why its Cohen's d may be undefined (zero variance in paired differences, near-zero transitions across all subjects).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(results="asis")
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
# Load required libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(pheatmap)
library(RColorBrewer)
library(corrplot)
library(gridExtra)
library(reshape2)
library(dotenv)
```

```{r}
# Function to get individual subject matrices of a session for statistical testing
get_subject_matrices <- function(df, session) {
  ses_data <- df[df$session == session, ]
  subjects <- unique(ses_data$subject)
  
  # Create a 3D array: subjects x from_CAP x to_CAP
  subject_matrices <- array(0, dim = c(length(subjects), k, k))
  
  for (s_idx in seq_along(subjects)) {
    subject <- subjects[s_idx]
    subj_data <- ses_data[ses_data$subject == subject, ]
    
    for (i in 1:k) {
      for (j in 1:k) {
        if (i != j) {
          prob_data <- subj_data[subj_data$from_CAP == paste0('CAP', i) & 
                                subj_data$to_CAP == paste0('CAP', j), ]$transition_probability
          
          if (length(prob_data) > 0) {
            subject_matrices[s_idx, i, j] <- prob_data[1]
          } else {
            subject_matrices[s_idx, i, j] <- NA
          }
        }
      }
    }
  }
  
  return(list(matrices = subject_matrices, subjects = subjects))
}
```

```{r}
# Function to get transition matrix for a session
get_transition_matrix <- function(df, session) {
  ses_data <- df[df$session == session, ]
  matrix_result <- matrix(0, nrow = k, ncol = k)
  
  for (i in 1:k) {
    for (j in 1:k) {
      if (i != j) {
        probs <- ses_data[ses_data$from_CAP == paste0('CAP', i) & 
                         ses_data$to_CAP == paste0('CAP', j), ]$transition_probability
        
        if (length(probs) > 0) {
          matrix_result[i, j] <- mean(probs, na.rm = TRUE)
        }
      } else {
        matrix_result[i, j] <- NA  # Diagonal elements set to NA
      }
    }
  }
  
  return(matrix_result)
}
```

# GLobal params

Dirs

```{r}
load_dot_env(file = "../.env")

BASE_DIR    <- Sys.getenv("BASE_DIR")
RESULTS_DIR <- Sys.getenv("RESULTS_DIR")

INPUT_DIR        <- file.path(BASE_DIR)
PLOTS_OUTPUT_DIR <- file.path(RESULTS_DIR, "main_figures", "05_caps_tp")
STATS_OUTPUT_DIR <- file.path(RESULTS_DIR, "stats", "02_caps")

dir.create(PLOTS_OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
dir.create(STATS_OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
```

```{r}
# Set parameters
k <- 7
subs <- c('Y01', 'Y02', 'Y03', 'Y04', 'Y05', 'Y06', 'Y07', 'Y08', 'Y09', 'Y10',
          'Y11', 'Y12', 'Y13', 'Y14', 'Y15', 'Y16', 'Y17', 'Y18', 'Y19', 'Y20')
sessions <- c(1, 2, 3)
sessions_dict <- c("1" = "Unilateral", "2" = "Bilateral", "3" = "Sham")
runs <- c(2)
runs_dict <- c("2" = "tDCS On")
runs_str <- "run-ON"

transition_df <- read_csv(file.path(INPUT_DIR, "caps_dynamics_run-ON", 
                                "caps_nclust-7", "CAP_transitions_full.csv"))

```

# Transition probs heatmaps

```{r, fig.height=5, fig.width=17}
# Modified create_heatmap function to control colorbar display
create_heatmap <- function(matrix_data, title, vmin, vmax, show_colorbar = TRUE) {
  # Convert matrix to long format for ggplot
  matrix_df <- expand.grid(From = 1:k, To = 1:k)
  matrix_df$Value <- as.vector(matrix_data)
  matrix_df$From <- factor(paste0("CAP", matrix_df$From))
  matrix_df$To <- factor(paste0("CAP", matrix_df$To))
  
  # Remove diagonal elements
  matrix_df <- matrix_df[matrix_df$From != matrix_df$To, ]
  
  p <- ggplot(matrix_df, aes(x = To, y = From, fill = Value)) +
    geom_tile(size = 0.8) +
    scale_fill_distiller(name = "Transition\nProbability\n", 
                         palette = "Oranges",
                         direction = 1,
                         limits = c(vmin, vmax),
                         na.value = "grey90",
                         guide = guide_colorbar(barwidth = 2, 
                                              barheight = 16,
                                              title.position = "top",
                                              title.hjust = 0.8,
                                              label.theme = element_text(size = 14),
                                              title.theme = element_text(size = 16, hjust = 0.5))) +
    geom_text(aes(label = sprintf("%.2f", Value)), 
              size = 18, 
              angle = -45,
              color = "black") +
    labs(x = "",
         y = "") +
    scale_y_discrete(limits = rev(levels(matrix_df$From))) +  # Reverse y-axis to put CAP1 at top
    theme_minimal() +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, size = 24, face = "bold"),
          axis.title = element_text(size = 24),
          legend.title = element_text(size = 16, face = "bold"),
          legend.text = element_text(size = 14), 
          panel.border = element_rect(color = "black", fill = "NA", size = 4))
  
  # Control colorbar display
  if (!show_colorbar) {
    p <- p + guides(fill = "none")
  }
  
  return(p)
}


all_values <- c()
for (ses_key in sessions) {
  trans_matrix <- get_transition_matrix(transition_df, ses_key)
  all_values <- c(all_values, as.vector(trans_matrix))
}

# Remove NA values and calculate min/max
all_values <- all_values[!is.na(all_values)]
vmin <- min(all_values)
vmax <- max(all_values)

vmin <- 0
vmax <- 0.5

cat(sprintf("Global min transition probability: %.3f\n", vmin))
cat(sprintf("Global max transition probability: %.3f\n", vmax))


# Create heatmaps for each condition
heatmap_plots <- list()
for (idx in seq_along(sessions)) {
  ses_key <- sessions[idx]
  ses_name <- sessions_dict[as.character(ses_key)]
  
  cat(sprintf("\nProcessing %s session...\n", ses_name))
  
  # Get transition matrix
  trans_matrix <- get_transition_matrix(transition_df, ses_key)
  
  # Create heatmap with colorbar (we'll extract and remove it later)
  p <- create_heatmap(trans_matrix, paste(ses_name, "tDCS"), vmin, vmax, TRUE)
  heatmap_plots[[idx]] <- p
  
  # Print summary statistics
  cat(sprintf("  Mean transition probability: %.3f\n", mean(trans_matrix, na.rm = TRUE)))
  cat(sprintf("  Max transition probability: %.3f\n", max(trans_matrix, na.rm = TRUE)))
  cat(sprintf("  Min transition probability (excl. diagonal): %.3f\n", min(trans_matrix, na.rm = TRUE)))
}

# Load required library for better plot arrangement
library(cowplot)

# Extract the legend from the last plot
legend <- get_legend(heatmap_plots[[length(sessions)]])

# Remove legend from all plots
plots_no_legend <- lapply(heatmap_plots, function(p) p + guides(fill = "none"))

# Combine plots without legends
plots_combined <- plot_grid(plotlist = plots_no_legend, ncol = 3, align = "hv")

# Add the single legend to the right with more space
combined_plot <- plot_grid(plots_combined, legend, ncol = 2, rel_widths = c(1, 0.15))

# Save the combined plot with larger dimensions
ggsave(file.path(PLOTS_OUTPUT_DIR, 'TP_raw_heatmaps_all_sessions.png'), 
       combined_plot, width = 17, height = 5, dpi = 400)

print(combined_plot)

# =============================================
# NEW CODE: Print and save individual heatmaps
# =============================================

cat("\n\nCreating individual heatmaps...\n")

# Print and save each heatmap individually (without colorbar)
for (idx in seq_along(sessions)) {
  ses_key <- sessions[idx]
  ses_name <- sessions_dict[as.character(ses_key)]
  
  cat(sprintf("Creating individual heatmap for %s session...\n", ses_name))
  
  # Create individual heatmap WITHOUT colorbar
  individual_plot <- heatmap_plots[[idx]] + guides(fill = "none")
  
  # Generate filename for individual plot
  individual_filename_png <- file.path(PLOTS_OUTPUT_DIR, paste0('TP_raw_heatmap_', 
                                                       tolower(ses_name), 
                                                       '.png'))
  
  # Save individual plot
  ggsave(individual_filename_png, individual_plot, width = 12, height = 12, dpi = 400)
  
  cat(sprintf("  Saved individual heatmap to: %s\n", individual_filename_png))
  
  # Print individual plot to console/viewer
  print(individual_plot)
}

# =============================================
# Create separate colorbar with large text
# =============================================

cat("\nCreating separate colorbar...\n")

# Create a proper standalone colorbar plot
colorbar_data <- data.frame(
  x = 1,
  y = seq(vmin, vmax, length.out = 100),
  fill = seq(vmin, vmax, length.out = 100)
)

colorbar_plot <- ggplot(colorbar_data, aes(x = x, y = y, fill = fill)) +
  geom_tile() +
  scale_fill_distiller(name = "", 
                       palette = "Oranges",
                       direction = 1,
                       limits = c(vmin, vmax),
                       breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                       guide = guide_colorbar(barwidth = 25, 
                                            barheight = 3)) +
  theme_void() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 45, face = "bold"),
        legend.text = element_text(size = 40),
        legend.margin = margin(t = 20, b = 20),
        plot.margin = margin(t = 20, b = 20, l = 20, r = 20)) +
  coord_fixed(ratio = 0.02) +
  guides(fill = guide_colorbar(title.position = "top",
                               raw.ulim= TRUE,
                               title.hjust = 0.5,
                               barwidth = 35,
                               barheight = 3))

# Save the colorbar
colorbar_filename_png <- file.path(PLOTS_OUTPUT_DIR, 'TP_raw_heatmaps_colorbar.png')

ggsave(colorbar_filename_png, colorbar_plot, width = 15, height = 5, dpi = 400)

cat(sprintf("Saved colorbar to: %s\n", colorbar_filename_png))

# Print colorbar
print(colorbar_plot)

cat("\nAll individual heatmaps and colorbar have been created and saved.\n")
```

# Cohens d plots of transition analysis

```{r helper_functions}
# Compute paired Cohen's d 
compute_cohens_d_paired <- function(data1, data2) {
  if (length(data1) < 2 || length(data2) < 2) {
    return(list(cohens_d = NA, mean_diff = NA, n_pairs = length(data1)))
  }
  dvals <- data1 - data2
  cohens_d_val <- mean(dvals, na.rm = TRUE) / stats::sd(dvals, na.rm = TRUE)
  mean_diff    <- mean(dvals, na.rm = TRUE)
  return(list(cohens_d = cohens_d_val, mean_diff = mean_diff, n_pairs = length(dvals)))
}
```

```{r perform_analysis}
# Compute Cohen's d for each CAP-pair transition across pairwise session comparisons

cat("=== COHEN'S D ANALYSIS ===\n")

# Convert to wide format (each CAP pair as a column)
tp_wide <- transition_df %>%
  mutate(CAP_pair = paste0(from_CAP, "_", to_CAP)) %>%
  pivot_wider(
    id_cols = c(subject, session),
    names_from = CAP_pair,
    values_from = transition_probability,
    values_fill = NA
  )

# Get all CAP pair column names
cap_pair_cols <- grep("^CAP[0-9]+_CAP[0-9]+$", names(tp_wide), value = TRUE)

cat(sprintf("Total CAP-to-CAP transitions found: %d\n", length(cap_pair_cols)))
cat(sprintf("Expected transitions (7x6): %d\n\n", 42))

# Define comparisons
comparisons <- list(
  list(
    title = "Unilateral - Sham",
    name = "unilateral",
    session1 = 1,
    session2 = 3
  ),
  list(
    title = "Bilateral - Sham",
    name = "bilateral",
    session1 = 2,
    session2 = 3
  ),
  list(
    title = "Bilateral - Unilateral",
    name = "bilateral_vs_unilateral",
    session1 = 2,
    session2 = 1
  )
)

all_test_results <- data.frame()

for (comp_idx in seq_along(comparisons)) {
  comp <- comparisons[[comp_idx]]

  cat(sprintf("Processing %s...\n", comp$title))

  cohens_d_matrix <- matrix(NA, nrow = k, ncol = k)
  effect_sizes    <- matrix(NA, nrow = k, ncol = k)

  n_calculated <- 0
  n_skipped    <- 0

  for (cap_pair in cap_pair_cols) {
    parts    <- strsplit(cap_pair, "_")[[1]]
    from_idx <- as.integer(gsub("CAP", "", parts[1]))
    to_idx   <- as.integer(gsub("CAP", "", parts[2]))

    session1_data <- tp_wide %>%
      filter(session == comp$session1) %>%
      select(subject, all_of(cap_pair))

    session2_data <- tp_wide %>%
      filter(session == comp$session2) %>%
      select(subject, all_of(cap_pair))

    paired_data <- inner_join(session1_data, session2_data, by = "subject", suffix = c("_1", "_2"))

    data1 <- paired_data[[paste0(cap_pair, "_1")]]
    data2 <- paired_data[[paste0(cap_pair, "_2")]]

    valid_mask  <- !is.na(data1) & !is.na(data2)
    data1_final <- data1[valid_mask]
    data2_final <- data2[valid_mask]

    if (length(data1_final) < 3) {
      n_skipped <- n_skipped + 1
      next
    }

    # Skip if all values are zero (no transitions occur)
    if (max(c(data1_final, data2_final)) < 0.001) {
      n_skipped <- n_skipped + 1
      next
    }

    result <- compute_cohens_d_paired(data1_final, data2_final)

    effect_sizes[from_idx, to_idx]    <- result$mean_diff
    cohens_d_matrix[from_idx, to_idx] <- result$cohens_d

    result_row <- data.frame(
      Comparison      = comp$title,
      Transition      = paste0("CAP", from_idx, " -> CAP", to_idx),
      Mean_Difference = result$mean_diff,
      Cohens_d        = result$cohens_d,
      n_pairs         = result$n_pairs,
      stringsAsFactors = FALSE
    )
    all_test_results <- rbind(all_test_results, result_row)

    n_calculated <- n_calculated + 1
  }

  cat(sprintf("  Successfully calculated: %d transitions\n", n_calculated))
  cat(sprintf("  Skipped: %d transitions\n\n", n_skipped))

  comparisons[[comp_idx]]$cohens_d    <- cohens_d_matrix
  comparisons[[comp_idx]]$effect_sizes <- effect_sizes
}

write.csv(all_test_results,
          file.path(STATS_OUTPUT_DIR, "cohens_d_transitions.csv"),
          row.names = FALSE)
cat(sprintf("Saved Cohen's d results to: %s\n",
            file.path(STATS_OUTPUT_DIR, "cohens_d_transitions.csv")))
```

```{r plotting_functions}
# Function to determine text color based on background intensity
get_text_color <- function(fill_value, max_abs_value) {
  normalized_value <- fill_value / max_abs_value
  intensity <- abs(normalized_value)
  
  if (intensity > 0.6) {
    return("white")
  } else {
    return("black")
  }
}

# Function to create Cohen's d heatmap
create_cohens_d_heatmap <- function(comp, show_colorbar = TRUE) {
  cohens_d_matrix <- comp$cohens_d
  
  # Create annotation matrix
  annot_matrix <- matrix("", nrow = k, ncol = k)
  text_color_matrix <- matrix("black", nrow = k, ncol = k)
  
  # Calculate max absolute Cohen's d for consistent scale
  max_cohens_d <- 0.6  # Fixed scale as in your original code
  
  for (i in 1:k) {
    for (j in 1:k) {
      if (i != j) {
        cohens_d_val <- cohens_d_matrix[i, j]
        
        if (!is.na(cohens_d_val)) {
          annot_text <- sprintf("%.2f", cohens_d_val)
          annot_matrix[i, j] <- annot_text
          text_color_matrix[i, j] <- get_text_color(cohens_d_val, max_cohens_d)
        }
      }
    }
  }
  
  # Convert to long format
  cohens_df <- expand.grid(From = 1:k, To = 1:k)
  cohens_df$Value <- as.vector(cohens_d_matrix)
  cohens_df$Annotation <- as.vector(annot_matrix)
  cohens_df$TextColor <- as.vector(text_color_matrix)
  cohens_df$From <- factor(paste0("CAP", cohens_df$From))
  cohens_df$To <- factor(paste0("CAP", cohens_df$To))
  
  # Remove diagonal elements AND rows with NA values
  cohens_df <- cohens_df[cohens_df$From != cohens_df$To & !is.na(cohens_df$Value), ]
  
  p <- ggplot(cohens_df, aes(x = To, y = From, fill = Value)) +
    geom_tile(size = 0.8) +
    scale_fill_gradient2(name = "Cohen's d",
                         low = "darkblue", mid = "white", high = "darkred",
                         midpoint = 0,
                         limits = c(-max_cohens_d, max_cohens_d),
                         na.value = "white",  # Make NA values white/transparent
                         guide = guide_colorbar(barwidth = 2, 
                                              barheight = 16,
                                              title.position = "top",
                                              title.hjust = 0.8,
                                              label.theme = element_text(size = 14),
                                              title.theme = element_text(size = 16, hjust = 0.5))) +
    geom_text(aes(label = Annotation, color = TextColor), 
              size = 18, 
              angle = -45) +
    scale_color_identity() +
    labs(x = "", y = "") +
    scale_y_discrete(limits = rev(levels(cohens_df$From))) +
    theme_minimal() +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, size = 24, face = "bold"),
          axis.title = element_text(size = 24),
          legend.title = element_text(size = 16, face = "bold"),
          legend.text = element_text(size = 14),
          panel.border = element_rect(color = "black", fill = NA, size = 4),
          panel.background = element_rect(fill = "white", color = NA))
  
  if (!show_colorbar) {
    p <- p + guides(fill = "none")
  }
  
  return(p)
}
```

```{r create_plots}
cat("\n\nCreating individual Cohen's d heatmaps...\n")

# Create and save individual heatmaps
for (idx in seq_along(comparisons)) {
  comp <- comparisons[[idx]]
  
  cat(sprintf("Creating heatmap for %s...\n", comp$title))
  
  # Create plot without colorbar
  p <- create_cohens_d_heatmap(comp, show_colorbar = FALSE)
  
  # Save plot
  filename <- file.path(PLOTS_OUTPUT_DIR, paste0('cohens_d_heatmap_', comp$name, '.png'))
  ggsave(filename, p, width = 12, height = 12, dpi = 400)
  
  cat(sprintf("  Saved to: %s\n", filename))
  
  # Print to console
  print(p)
}

# Create colorbar
cat("\nCreating separate colorbar...\n")

colorbar_data <- data.frame(
  x = 1,
  y = seq(-0.6, 0.6, length.out = 100),
  fill = seq(-0.6, 0.6, length.out = 100)
)

colorbar_plot <- ggplot(colorbar_data, aes(x = x, y = y, fill = fill)) +
  geom_tile() +
  scale_fill_gradient2(name = "Cohen's d", 
                       low = "darkblue", mid = "white", high = "darkred",
                       midpoint = 0,
                       limits = c(-0.6, 0.6),
                       breaks = c(-0.6, -0.3, 0, 0.3, 0.6),
                       guide = guide_colorbar(barwidth = 30, 
                                            barheight = 3,
                                            title.position = "top",
                                            title.hjust = 0.5,
                                            label.theme = element_text(size = 40),
                                            title.theme = element_text(size = 45, hjust = 0.5, face = "bold"))) +
  theme_void() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 45, face = "bold"),
        legend.text = element_text(size = 40),
        legend.margin = margin(t = 20, b = 20),
        plot.margin = margin(t = 20, b = 20, l = 20, r = 20)) +
  coord_fixed(ratio = 0.02)

# Save colorbar
colorbar_filename <- file.path(PLOTS_OUTPUT_DIR, 'cohens_d_colorbar.png')
ggsave(colorbar_filename, colorbar_plot, width = 12, height = 4, dpi = 400)

cat(sprintf("Saved colorbar to: %s\n", colorbar_filename))
print(colorbar_plot)
```

Diagnostic: CAP7 -\> CAP6 undefined Cohen's d

```{r}
cat("=== DIAGNOSTIC: CAP7 -> CAP6 TRANSITION ===\n\n")

# Pull raw values for every session
cap7_to_6 <- transition_df %>%
  filter(from_CAP == "CAP7" & to_CAP == "CAP6") %>%
  select(subject, session, transition_probability) %>%
  arrange(subject, session)

cat("Raw data (all sessions):\n")
print(cap7_to_6)

# Per-session summary: mean, sd, n, n_unique
cat("\nPer-session summary:\n")
print(
  cap7_to_6 %>%
    group_by(session) %>%
    summarise(
      mean     = mean(transition_probability, na.rm = TRUE),
      sd       = sd(transition_probability, na.rm = TRUE),
      n        = n(),
      n_unique = n_distinct(transition_probability),
      n_zero   = sum(transition_probability < 0.001, na.rm = TRUE),
      .groups  = "drop"
    )
)

# For each comparison, show the paired differences that go into Cohen's d
cat("\nPaired differences per comparison:\n")
tp_wide_diag <- transition_df %>%
  mutate(CAP_pair = paste0(from_CAP, "_", to_CAP)) %>%
  pivot_wider(
    id_cols     = c(subject, session),
    names_from  = CAP_pair,
    values_from = transition_probability,
    values_fill = NA
  )

```
