---
title: "Statistical analysis corerelations between CAPs dynamics under sham and paramters of behavioral taks under sham.Rmd"
output:
  pdf_document: default
  html_document: default
date: "2025-06-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(results="asis")
knitr::opts_chunk$set(warning = FALSE)
```

## Overview

This notebook investigates whether CAP dynamics under sham stimulation are associated with behavioral performance, also under sham — asking whether brain–behavior associations exist independently of active stimulation.

To assess functional relevance, Spearman rank correlations are computed between CAP metrics (occurrence rate, dwell time for CAP4, CAP1→CAP7 transition probability) and behavioral parameters from four motor tasks (APM, VGR, OH, BOB), restricted to sham sessions.

**Analysis steps:**

1.  **Load CAP data** — occurrence rate, dwell time, and transition probability CSVs (`caps_dynamics_run-ON/caps_nclust-7/`).
2.  **Load behavioral data** — anonymized CSVs for APM, VGR, OH, and BOB from `BEH_DATA_ANON_DIR/csv/`; young participants only.
3.  **Correlate CAP4 OC/DT with behavior** — Spearman correlations in the sham session for all behavioral parameters.
4.  **Correlate CAP1→CAP7 TP with behavior** — same approach for transition probability.
5.  **Save results** — all and significant correlations saved to `results/stats/03_caps_beh_sham/`.
6.  **Plot significant correlations** — scatter plots with regression lines saved to `results/main_figures/06_caps_beh_sham/`.

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(ggplot2)
library(dplyr)
library(janitor)
library(ggpubr)
library(rstatix)
library(tidyverse)
library(gtsummary)
library(knitr)
library(ggrepel)
library(rstatix)
library(sjPlot)
library(sjtable2df)
library(GGally)
library(dplyr)
```

```{r}
# Function to prepare data (reusing from your code)
prepare_df <- function(file_path) {
  # Read data from the provided file path
  data <- read.csv(file_path)

  # Clean up columns: remove original session/run and rename _name columns
  data <- data %>%
    select(-session, -run) %>%
    rename(session = session_name, run = run_name)

  # Filter to include only "On" data
  data_on <- data %>% filter(run == "tDCS On")

  # Convert factors with proper reference levels
  data_on$session <- factor(data_on$session, levels = c("Sham", "Unilateral", "Bilateral"))
  data_on$subject <- factor(data_on$subject)
  return(data_on)
}
compute_session_deltas <- function(df, num_vars) {
  # Create a new dataframe containing just the subjects
  delta_df <- data.frame(subject = unique(df$subject))

  # For each subject and each numerical variable, compute the delta values
  for (var in num_vars) {
    # Initialize columns for each delta comparison
    delta_df[paste0(var, "_bi_sham")] <- NA
    delta_df[paste0(var, "_bi_uni")] <- NA
    delta_df[paste0(var, "_uni_sham")] <- NA

    # Loop through each subject
    for (subj in unique(df$subject)) {
      # Extract data for the current subject
      subj_data <- df[df$subject == subj, ]

      # Get values for each session
      sham_val <- subj_data[subj_data$session == "Sham", var]
      bi_val <- subj_data[subj_data$session == "Bilateral", var]
      uni_val <- subj_data[subj_data$session == "Unilateral", var]

      # Compute deltas
      if (length(sham_val) > 0 && length(bi_val) > 0) {
        delta_df[delta_df$subject == subj, paste0(var, "_bi_sham")] <- bi_val - sham_val
      }

      if (length(bi_val) > 0 && length(uni_val) > 0) {
        delta_df[delta_df$subject == subj, paste0(var, "_bi_uni")] <- bi_val - uni_val
      }

      if (length(uni_val) > 0 && length(sham_val) > 0) {
        delta_df[delta_df$subject == subj, paste0(var, "_uni_sham")] <- uni_val - sham_val
      }
    }
  }

  return(delta_df)
}
```

## Global params

Global number of permutations and dirs

```{r}
library(dotenv)
load_dot_env(file = "../.env")

BASE_DIR          <- Sys.getenv("BASE_DIR")
RESULTS_DIR       <- Sys.getenv("RESULTS_DIR")
BEH_DATA_ANON_DIR <- Sys.getenv("BEH_DATA_ANON_DIR")

INPUT_DIR_BEH  <- file.path(BEH_DATA_ANON_DIR, "csv")
INPUT_DIR_CAPS <- file.path(BASE_DIR)

OUTPUT_DIR       <- file.path(RESULTS_DIR, "stats", "03_caps_beh")
PLOTS_OUTPUT_DIR <- file.path(RESULTS_DIR, "main_figures", "06_caps_beh")

dir.create(OUTPUT_DIR,       recursive = TRUE, showWarnings = FALSE)
dir.create(PLOTS_OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
```

# Load CPAs data

```{r}
k=7
k7_df_occ <- prepare_df(file.path(INPUT_DIR_CAPS, "caps_dynamics_run-ON", 
                                 paste0("caps_nclust-", k), "CAP_occurence_times.csv"))

k7_df_dt <- prepare_df(file.path(INPUT_DIR_CAPS, "caps_dynamics_run-ON", 
                                paste0("caps_nclust-", k), "CAP_dwelltime.csv"))

str(k7_df_occ)
head(k7_df_occ)

str(k7_df_dt)
head(k7_df_dt)
```

# Load CPAs transition prob data

```{r}
cap_tp_full <- prepare_df(file.path(INPUT_DIR_CAPS, "caps_dynamics_run-ON",
                                "caps_nclust-7", "CAP_transitions_full.csv"))

str(cap_tp_full)
head(cap_tp_full)
```

```{r}
cap_tp_1_7 <- cap_tp_full %>% filter(from_CAP=="CAP1" & to_CAP=="CAP7")

str(cap_tp_1_7)
head(cap_tp_1_7)
```

# Load behavioral data

## APM

Left hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH, "APM_left_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH, "APM_left_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH, "APM_left_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()
comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))
comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  abs_error_x_m,
                                  abs_error_y_m,
                                  variability_x_m,
                                  variability_y_m,
                                  contraction_expansion_ratio_x,
                                  contraction_expansion_ratio_y,
                                  shift_x_m,
                                  shift_y_m)


# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_l <- comb_data
table(comb_data_l$stimulation_condition)
head(comb_data_l)
```

Righ hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"APM_right_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"APM_right_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"APM_right_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()
comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))



comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  abs_error_x_m,
                                  abs_error_y_m,
                                  variability_x_m,
                                  variability_y_m,
                                  contraction_expansion_ratio_x,
                                  contraction_expansion_ratio_y,
                                  shift_x_m,
                                  shift_y_m)


#co# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_r <- comb_data
table(comb_data_r$stimulation_condition)
head(comb_data_r)
```

```{r}
conatinated_apm <- rbind(comb_data_l, comb_data_r)
head(conatinated_apm)
tail(conatinated_apm)
str(conatinated_apm)
```

```{r}
apm_wide <- conatinated_apm %>%
  mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH")) %>%
  pivot_wider(
    id_cols = c("subject", "neuron_id", "handedness", "session"),
    names_from = arm_prefix,
    values_from = c(
      "fraction_complete",
      "abs_error_x_m",
      "abs_error_y_m",
      "variability_x_m",
      "variability_y_m",
      "contraction_expansion_ratio_x",
      "contraction_expansion_ratio_y",
      "shift_x_m",
      "shift_y_m"
    ),
    names_glue = "{arm_prefix}_{.value}"
  )

str(apm_wide)

head(apm_wide)
```

```{r, results='hide'}
apm_behavior_vars <- c(
  "abs_error_x_m",
  "abs_error_y_m",
      "variability_x_m",
      "variability_y_m",
      "contraction_expansion_ratio_x",
      "contraction_expansion_ratio_y",
      "shift_x_m",
      "shift_y_m"
                       )

apm_behavior_vars_lh <- paste0("LH_", apm_behavior_vars)
apm_behavior_vars_rh <- paste0("RH_", apm_behavior_vars)

# Combine both LH and RH behavior variables
apm_behavior_vars_both_hands <- c(apm_behavior_vars_lh, apm_behavior_vars_rh)
```

## VGR

Left hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_left_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_left_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_left_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)


comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  posture_speed_m_s,
                                  reaction_time_s,
                                  initial_direction_angle_rad,
                                  initial_distance_ratio,
                                  initial_speed_ratio,
                                  speed_maxima_count,
                                  movement_time_s,
                                  path_length_ratio,
                                  false_starts)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_l <- comb_data
# Verifying the result
table(comb_data_l$stimulation_condition, comb_data_l$session)
head(comb_data_l)
```

Right hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_right_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_right_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_right_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  posture_speed_m_s,
                                  reaction_time_s,
                                  initial_direction_angle_rad,
                                  initial_distance_ratio,
                                  initial_speed_ratio,
                                  speed_maxima_count,
                                  movement_time_s,
                                  path_length_ratio,
                                  false_starts)


comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_r <- comb_data
# Verifying the result
table(comb_data_r$stimulation_condition, comb_data_r$session)
head(comb_data_r)
```

```{r}
conatinated_vgr <- rbind(comb_data_l, comb_data_r)
head(conatinated_vgr)
tail(conatinated_vgr)
table(conatinated_vgr$active_arm, conatinated_vgr$session)
```

```{r}
vgr_wide <- conatinated_vgr %>%
  mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH")) %>%
  pivot_wider(
    id_cols = c("subject", "neuron_id", "handedness", "session"),
    names_from = arm_prefix,
    values_from = c("fraction_complete",
                    "posture_speed_m_s",
                    "reaction_time_s",
                    "initial_direction_angle_rad",
                    "initial_distance_ratio",
                    "initial_speed_ratio",
                    "speed_maxima_count",
                    "movement_time_s",
                    "path_length_ratio",
                    "false_starts"
    ),
    names_glue = "{arm_prefix}_{.value}"
  )

str(vgr_wide)

head(vgr_wide)
```

```{r, results='hide'}
cap_vars <- c("CAP4")
vgr_behavior_vars <- c("posture_speed_m_s", 
                       "reaction_time_s", 
                       "initial_direction_angle_rad", 
                       "initial_distance_ratio", 
                       "initial_speed_ratio", 
                       "speed_maxima_count",
                       "movement_time_s", 
                       "path_length_ratio", 
                       "false_starts")

vgr_behavior_vars_lh <- paste0("LH_", vgr_behavior_vars)
vgr_behavior_vars_rh <- paste0("RH_", vgr_behavior_vars)

# Combine both LH and RH behavior variables
vgr_behavior_vars_both_hands <- c(vgr_behavior_vars_lh, vgr_behavior_vars_rh)
```

## OH

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"OH_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"OH_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"OH_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete,
                                  handedness, stimulation_condition, active_arm,
                                  total_hits,
                                  hits_with_left,
                                  hits_with_right,
                                  hand_bias_of_hits,
                                  median_error,
                                  miss_bias,
                                  hand_speed_right_m_s,
                                  hand_speed_left_m_s,
                                  hand_speed_bias,
                                  movement_area_right_hand_m_2, 
                                  movement_area_left_hand_m_2,
                                  movement_area_bias,
                                  hand_transition,
                                  hand_selection_overlap)


comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

# Verifying the result
oh_data <- comb_data
table(oh_data$stimulation_condition, oh_data$session)
head(oh_data)
```

```{r}
cap_vars <- c("CAP4")
oh_behavior_vars <- c("total_hits", 
                   "hits_with_left", 
                   "hits_with_right", 
                   "hand_bias_of_hits",
                   "median_error", 
                   "miss_bias", 
                   "hand_speed_right_m_s",
                   "hand_speed_left_m_s", 
                   "hand_speed_bias", 
                   "movement_area_right_hand_m_2", 
                   "movement_area_left_hand_m_2", 
                   "movement_area_bias", 
                   "hand_transition",
                   "hand_selection_overlap")

```

## BOB

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"BOB_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"BOB_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"BOB_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  x1_targets_completed,
                                  x2_targets_completed,
                                  x3_targets_completed,
                                  #x2_drops,#variance=0
                                  x3_drops,#
                                  #x2_drops_targets,##variance=0
                                  x3_drops_targets,#
                                  x1_mean_movement_time_s,
                                  x2_mean_movement_time_s,
                                  x3_mean_movement_time_s,
                                  x1_right_hand_speed_maxima,
                                  x2_right_hand_speed_maxima,
                                  x3_right_hand_speed_maxima,
                                  x1_left_hand_speed_maxima,
                                  x2_left_hand_speed_maxima,
                                  x3_left_hand_speed_maxima,
                                  x1_mean_bar_angle_rad,
                                  x2_mean_bar_angle_rad,
                                  x3_mean_bar_angle_rad,
                                  x1_bar_length_variability,#
                                  x2_bar_length_variability,#
                                  x3_bar_length_variability,#
                                  x1_reaction_time_abs_diff_s,
                                  x1_hand_speed_diff_m_s,
                                  x2_hand_speed_diff_m_s,
                                  x3_hand_speed_diff_m_s
                                  )

bob_behavior_vars <- c(
  "x1_targets_completed",
  "x2_targets_completed",
  "x3_targets_completed",
  #"x2_drops", #variance=0
  "x3_drops",
  #"x2_drops_targets", #variance=0
  "x3_drops_targets",
  "x1_mean_movement_time_s",
  "x2_mean_movement_time_s",
  "x3_mean_movement_time_s",
  "x1_right_hand_speed_maxima",
  "x2_right_hand_speed_maxima",
  "x3_right_hand_speed_maxima",
  "x1_left_hand_speed_maxima",
  "x2_left_hand_speed_maxima",
  "x3_left_hand_speed_maxima",
  "x1_mean_bar_angle_rad",
  "x2_mean_bar_angle_rad",
  "x3_mean_bar_angle_rad",
  "x1_bar_length_variability",
  "x2_bar_length_variability",
  "x3_bar_length_variability",
  "x1_reaction_time_abs_diff_s",
  "x1_hand_speed_diff_m_s",
  "x2_hand_speed_diff_m_s",
  "x3_hand_speed_diff_m_s"
)

# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(across(all_of(bob_behavior_vars), as.numeric))

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

bob_data <- comb_data
# Verifying the result
table(bob_data$stimulation_condition,bob_data$session)
head(bob_data)
```

# Correlate with CAP4

```{r}
# Function to correlate CAP4 with behavioral variables in Sham condition
correlate_sham_cap_behavior <- function(cap_data, behavior_data, behavior_vars, task_name, cap_metric, method = "spearman") {
  
  results <- data.frame()
  
  # Merge CAP and behavior data
  merged_data <- merge(cap_data, behavior_data, by = c("subject", "session"))
  
  # Filter for Sham condition only
  sham_data <- merged_data %>% filter(session == "Sham")
  
  if (nrow(sham_data) < 5) {
    cat("Not enough Sham data for", task_name, "\n")
    return(data.frame())
  }
  
  # Correlate CAP4 with each behavioral variable
  for (var in behavior_vars) {
    if (var %in% names(sham_data)) {
      # Remove missing data
      clean_data <- sham_data[complete.cases(sham_data[c("CAP4", var)]), ]
      
      if (nrow(clean_data) >= 5) {
        # Calculate correlation
        cor_test <- cor.test(clean_data$CAP4, clean_data[[var]], method = method)
        
        # Handle confidence intervals (only available for Pearson)
        if (method == "pearson" && !is.null(cor_test$conf.int)) {
          ci_lower <- cor_test$conf.int[1]
          ci_upper <- cor_test$conf.int[2]
        } else {
          ci_lower <- NA
          ci_upper <- NA
        }
        
        # Store results
        results <- rbind(results, data.frame(
          task = task_name,
          cap_metric = cap_metric,
          parameter = var,
          r_value = as.numeric(cor_test$estimate),
          p_value = cor_test$p.value,
          n_obs = nrow(clean_data),
          ci_lower = ci_lower,
          ci_upper = ci_upper,
          method = method,
          stringsAsFactors = FALSE
        ))
      }
    }
  }
  
  return(results)
}


# Load all data
cat("Loading data...\n")
apm_data <- apm_wide
vgr_data <- vgr_wide
oh_data <- oh_data
bob_data <- bob_data
apm_behavior_vars <- apm_behavior_vars_both_hands
vgr_behavior_vars <- vgr_behavior_vars_both_hands 

# Run correlations for all tasks and both CAP metrics
cat("Running correlations...\n")

all_sham_correlations <- rbind(
  # Occurrence Rate
  correlate_sham_cap_behavior(k7_df_occ, apm_data, apm_behavior_vars, "APM", "Occurrence"),
  correlate_sham_cap_behavior(k7_df_occ, vgr_data, vgr_behavior_vars, "VGR", "Occurrence"),
  correlate_sham_cap_behavior(k7_df_occ, oh_data, oh_behavior_vars, "OH", "Occurrence"),
  correlate_sham_cap_behavior(k7_df_occ, bob_data, bob_behavior_vars, "BOB", "Occurrence"),
  
  # Dwell Time
  correlate_sham_cap_behavior(k7_df_dt, apm_data, apm_behavior_vars, "APM", "Dwell_Time"),
  correlate_sham_cap_behavior(k7_df_dt, vgr_data, vgr_behavior_vars, "VGR", "Dwell_Time"),
  correlate_sham_cap_behavior(k7_df_dt, oh_data, oh_behavior_vars, "OH", "Dwell_Time"),
  correlate_sham_cap_behavior(k7_df_dt, bob_data, bob_behavior_vars, "BOB", "Dwell_Time")
)

# Add significance indicators
all_sham_correlations$significance <- case_when(
  all_sham_correlations$p_value < 0.001 ~ "***",
  all_sham_correlations$p_value < 0.01 ~ "**",
  all_sham_correlations$p_value < 0.05 ~ "*",
  TRUE ~ ""
)

# Display results
cat("Summary of Sham Condition Correlations (CAP4 vs Behavioral Parameters):\n")
cat("Total correlations computed:", nrow(all_sham_correlations), "\n")
cat("Significant correlations (p < 0.05):", sum(all_sham_correlations$p_value < 0.05), "\n")

# Show significant results
significant_sham_oc_dt <- all_sham_correlations %>% 
  filter(p_value < 0.05) %>%
  arrange(p_value)

if (nrow(significant_sham_oc_dt) > 0) {
  cat("\nSignificant correlations:\n")
  print(significant_sham_oc_dt[, c("task", "cap_metric", "parameter", "r_value", "p_value", "significance")])
} else {
  cat("\nNo significant correlations found.\n")
}

```

# Correlate with CAP1-\>CAP7 TP

```{r}
# Function to correlate transition probability with behavioral variables in Sham condition
correlate_sham_cap_behavior <- function(cap_data, behavior_data, behavior_vars, task_name, cap_metric, method = "spearman") {
  
  results <- data.frame()
  
  # Merge CAP and behavior data
  merged_data <- merge(cap_data, behavior_data, by = c("subject", "session"))
  
  # Filter for Sham condition only
  sham_data <- merged_data %>% filter(session == "Sham")
  
  if (nrow(sham_data) < 5) {
    cat("Not enough Sham data for", task_name, "\n")
    return(data.frame())
  }
  
  # Correlate CAP4 with each behavioral variable
  for (var in behavior_vars) {
    if (var %in% names(sham_data)) {
      # Remove missing data
      clean_data <- sham_data[complete.cases(sham_data[c("transition_probability", var)]), ]
      
      if (nrow(clean_data) >= 5) {
        # Calculate correlation
        cor_test <- cor.test(clean_data$transition_probability, clean_data[[var]], method = method)
        
        # Handle confidence intervals (only available for Pearson)
        if (method == "pearson" && !is.null(cor_test$conf.int)) {
          ci_lower <- cor_test$conf.int[1]
          ci_upper <- cor_test$conf.int[2]
        } else {
          ci_lower <- NA
          ci_upper <- NA
        }
        
        # Store results
        results <- rbind(results, data.frame(
          task = task_name,
          cap_metric = cap_metric,
          parameter = var,
          r_value = as.numeric(cor_test$estimate),
          p_value = cor_test$p.value,
          n_obs = nrow(clean_data),
          ci_lower = ci_lower,
          ci_upper = ci_upper,
          method = method,
          stringsAsFactors = FALSE
        ))
      }
    }
  }
  
  return(results)
}



# Run correlations for all tasks and both CAP metrics
cat("Running correlations...\n")

all_sham_tp_correlations <- rbind(
  # Occurrence Rate
  correlate_sham_cap_behavior(cap_tp_1_7, apm_data, apm_behavior_vars, "APM", "transition_probability"),
  correlate_sham_cap_behavior(cap_tp_1_7, vgr_data, vgr_behavior_vars, "VGR", "transition_probability"),
  correlate_sham_cap_behavior(cap_tp_1_7, oh_data, oh_behavior_vars, "OH", "transition_probability"),
  correlate_sham_cap_behavior(cap_tp_1_7, bob_data, bob_behavior_vars, "BOB", "transition_probability")
)

# Add significance indicators
all_sham_tp_correlations$significance <- case_when(
  all_sham_tp_correlations$p_value < 0.001 ~ "***",
  all_sham_tp_correlations$p_value < 0.01 ~ "**",
  all_sham_tp_correlations$p_value < 0.05 ~ "*",
  TRUE ~ ""
)

# Display results
cat("Summary of Sham Condition Correlations (CAP4 vs Behavioral Parameters):\n")
cat("Total correlations computed:", nrow(all_sham_tp_correlations), "\n")
cat("Significant correlations (p < 0.05):", sum(all_sham_tp_correlations$p_value < 0.05), "\n")

# Show significant results
significant_sham_tp <- all_sham_tp_correlations %>% 
  filter(p_value < 0.05) %>%
  arrange(p_value)

if (nrow(significant_sham_tp) > 0) {
  cat("\nSignificant correlations:\n")
  print(significant_sham_tp[, c("task", "cap_metric", "parameter", "r_value", "p_value", "significance")])
} else {
  cat("\nNo significant correlations found.\n")
}

```

## Summary

```{r}
sham_all_metrics_sig_corrs <- rbind(significant_sham_oc_dt, significant_sham_tp)
str(sham_all_metrics_sig_corrs)
head(sham_all_metrics_sig_corrs, 8)
```

## Save

```{r}
all_results <- rbind(all_sham_correlations, all_sham_tp_correlations) %>%
  rename(metric = cap_metric, correlation = r_value, sig = significance) %>%
  mutate(r_squared = correlation^2) %>%
  dplyr::select(task, metric, parameter, correlation, p_value, r_squared, n_obs, sig) %>%
  arrange(p_value)

write.csv(all_results, file.path(OUTPUT_DIR, "sham_correlations_data.csv"), row.names = FALSE)
```

```{r, fig.width=14, fig.height=4}
# --- Step 1: Load libraries ---
# Load the package for nested facets
library(ggh4x) 

# --- Step 3: Prepare all CAP data in a long format ---
# We only need the metrics that were significant
cap_occ_long <- k7_df_occ %>%
  filter(session == "Sham") %>%
  select(subject, CAP4) %>%
  rename(value = CAP4) %>%
  mutate(cap_metric = "Occurrence")

cap_tp_long <- cap_tp_1_7 %>%
  filter(session == "Sham") %>%
  select(subject, transition_probability) %>%
  rename(value = transition_probability) %>%
  mutate(cap_metric = "transition_probability")

# Combine all *relevant* CAP data. 
# k7_df_dt (Dwell Time) is no longer needed here since it had no sig. correlations.
all_cap_data_long <- rbind(cap_occ_long, cap_tp_long)

# --- Step 4: Prepare all Behavioral data in a long format ---
# We only need the data frames and variables that were significant
apm_data_long <- apm_data %>%
  filter(session == "Sham") %>%
  pivot_longer(
    cols = all_of(apm_behavior_vars_both_hands),
    names_to = "parameter",
    values_to = "beh_value"
  ) %>%
  mutate(task = "APM") %>%
  select(subject, task, parameter, beh_value)

vgr_data_long <- vgr_data %>%
  filter(session == "Sham") %>%
  pivot_longer(
    cols = all_of(vgr_behavior_vars_both_hands),
    names_to = "parameter",
    values_to = "beh_value"
  ) %>%
  mutate(task = "VGR") %>%
  select(subject, task, parameter, beh_value)

bob_data_long <- bob_data %>%
  filter(session == "Sham") %>%
  pivot_longer(
    cols = all_of(bob_behavior_vars),
    names_to = "parameter",
    values_to = "beh_value"
  ) %>%
  mutate(task = "BOB") %>%
  select(subject, task, parameter, beh_value)

# Combine all behavioral data
all_beh_data_long <- rbind(apm_data_long, vgr_data_long, bob_data_long)

# --- Step 5: Create the final plotting data frame ---
# Join significant correlations with CAP data
plot_data_step1 <- inner_join(
  sham_all_metrics_sig_corrs,
  all_cap_data_long,
  by = "cap_metric"
)

# Join with behavioral data
plot_data_final <- inner_join(
  plot_data_step1,
  all_beh_data_long,
  by = c("subject", "task", "parameter")
) %>%
  mutate(
    # Remap cap_metric names for the title per your request
    cap_metric_title = case_when(
      cap_metric == "Occurrence" ~ "CAP4 OC",
      cap_metric == "transition_probability" ~ "CAP1 to CAP7 TP",
      TRUE ~ cap_metric # Fallback
    ),
    
    # Create the text label for the plot
    plot_label = sprintf("rho ~ '=' ~ %.2f*',' ~ p ~ '=' ~ %.3f", r_value, p_value)
  )


plot_data_final <- plot_data_final %>%
  mutate(
    cap_metric_title = fct_relevel(cap_metric_title,
                                   "CAP4 OC", "CAP1 to CAP7 TP"),
    task = fct_relevel(task,c("VGR", "BOB", "APM")))
head(plot_data_final)
tail(plot_data_final)
```

```{r, fig.width=14, fig.height=4}

p_sham <- ggplot(plot_data_final, aes(x = value, y = beh_value)) +
  geom_point(color = "black") +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "gray80", alpha = 0.2) +
  
  # Add correlation text (rho and p-value)
  geom_text(
    data = distinct(plot_data_final, cap_metric_title, task, parameter, plot_label),
    aes(label = plot_label),
    x = -Inf, y = Inf, hjust = -0.1, vjust = 1.5,
    size = 3, parse = TRUE
  ) +
  
  # Use facet_nested_wrap to create hierarchical strip titles
  ggh4x::facet_nested_wrap(
    ~ cap_metric_title + task + parameter,
    nrow = 1,
    scales = "free" # Keep scales free for each plot
  ) +
  
  # Add axis labels
  labs(
    x = "CAP Metric Value (Sham Condition)",
    y = "Behavioral Parameter Value (Sham Condition)"
  ) +
  
  # Apply a clean, journal-ready theme
  theme_classic() +
  theme(
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    axis.line = element_line(color = "black"),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 8),
    
    # Style the nested strip titles
    strip.background = element_rect(color = "black", fill = "grey90"),
    strip.text = element_text(size = 8, face = "bold", margin = margin(2, 2, 2, 2)),
    
    # Add a small space between the nested strips
    ggh4x.facet.nestline = element_line(color = "black"),
    
    # Adjust the horizontal spacing between panels
    panel.spacing.x = unit(1.5, "lines") 
  )

print(p_sham)

ggsave(
  file.path(PLOTS_OUTPUT_DIR, "Sham_correlations_clean_wide.png"),
  p_sham,
  width = 14,
  height = 4,
  dpi = 600,
  bg = "white"
)
```

```{r, fig.width=15, fig.height=3}

p_sham_clean <- ggplot(plot_data_final, aes(x = value, y = beh_value)) +
  geom_point(color = "black") +
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "gray60", alpha = 0.2) +
  
  # Add correlation text (rho and p-value)
  # geom_text(
  #   data = distinct(plot_data_final, cap_metric_title, task, parameter, plot_label),
  #   aes(label = plot_label),
  #   x = -Inf, y = Inf, hjust = -0.1, vjust = 1.5,
  #   size = 5, parse = TRUE
  # ) +
  
  # Use facet_nested_wrap to create hierarchical strip titles
  ggh4x::facet_nested_wrap(
    ~ cap_metric_title + task + parameter,
    nrow = 1,
    scales = "free" # Keep scales free for each plot
  ) +
  
  labs(x = NULL, y = NULL) +
  theme_classic() +
  
  # Remove all titles, text, and backgrounds 
  theme(
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
    axis.line = element_line(color = "black"),
    
    # Keep axis tick text (the numbers) but remove titles
    axis.title = element_blank(), 
    axis.text = element_text(size = 14),
    
    # Remove all strip text and backgrounds
    strip.background = element_blank(),
    strip.text = element_blank(),
    
    # Remove the nesting line
    ggh4x.facet.nestline = element_blank(),
    
    # Keep the panel spacing
    panel.spacing.x = unit(1.5, "lines") 
  )

print(p_sham_clean)

# Save clean plot for photoshop
ggsave(
  file.path(PLOTS_OUTPUT_DIR, "Sham_correlations_CLEAN_for_photoshop.png"),
  p_sham_clean,
  width = 15,
  height = 2.5,
  dpi = 600,
  bg = "white"
)
```
