---
title: "CAPS beh corr"
output:
  html_document:
    df_print: paged
---

## Overview

This notebook tests whether tDCS-modulated CAP dynamics are associated with motor behavior during stimulation, above and beyond baseline (sham) brain–behavior associations.

Partial Spearman correlations are computed between CAP metrics under bilateral tDCS and behavioral performance, controlling for both the sham CAP value and the sham behavioral value for each participant.

**Analysis steps:**

1. **Load CAP data** — occurrence rate and CAP1→CAP7 transition probability CSVs (`caps_dynamics_run-ON/caps_nclust-7/`).
2. **Load behavioral data** — anonymized CSVs for APM, VGR, OH, and BOB; young participants only.
3. **Run partial correlations** — bilateral tDCS session, controlling for sham baseline (CAP and behavior), for each task × metric combination.
4. **Save results** — all bilateral partial correlations saved to `results/stats/03_caps_beh/bilateral_partial_corr_data.csv`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(results="asis")
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
library(ggplot2)
library(tidyr)
library(patchwork)
library(ggplot2)
library(dplyr)
library(janitor)
library(ggpubr)
library(rstatix)
library(tidyverse)
library(gtsummary)
library(knitr)
library(ggrepel)
library(rstatix)
library(sjPlot)
library(sjtable2df)
library(GGally)
library(dplyr)
```

```{r}
# Function to prepare data (reusing from your code)
prepare_df <- function(file_path) {
  # Read data from the provided file path
  data <- read.csv(file_path)

  # Clean up columns: remove original session/run and rename _name columns
  data <- data %>%
    dplyr:: select(-session, -run) %>%
    rename(session = session_name, run = run_name)

  # Filter to include only "On" data
  data_on <- data %>% dplyr::filter(run == "tDCS On")

  # Convert factors with proper reference levels
  data_on$session <- factor(data_on$session, levels = c("Sham", "Unilateral", "Bilateral"))
  data_on$subject <- factor(data_on$subject)
  return(data_on)
}
compute_session_deltas <- function(df, num_vars) {
  # Create a new dataframe containing just the subjects
  delta_df <- data.frame(subject = unique(df$subject))

  # For each subject and each numerical variable, compute the delta values
  for (var in num_vars) {
    # Initialize columns for each delta comparison
    delta_df[paste0(var, "_bi_sham")] <- NA
    delta_df[paste0(var, "_bi_uni")] <- NA
    delta_df[paste0(var, "_uni_sham")] <- NA

    # Loop through each subject
    for (subj in unique(df$subject)) {
      # Extract data for the current subject
      subj_data <- df[df$subject == subj, ]

      # Get values for each session
      sham_val <- subj_data[subj_data$session == "Sham", var]
      bi_val <- subj_data[subj_data$session == "Bilateral", var]
      uni_val <- subj_data[subj_data$session == "Unilateral", var]

      # Compute deltas
      if (length(sham_val) > 0 && length(bi_val) > 0) {
        delta_df[delta_df$subject == subj, paste0(var, "_bi_sham")] <- bi_val - sham_val
      }

      if (length(bi_val) > 0 && length(uni_val) > 0) {
        delta_df[delta_df$subject == subj, paste0(var, "_bi_uni")] <- bi_val - uni_val
      }

      if (length(uni_val) > 0 && length(sham_val) > 0) {
        delta_df[delta_df$subject == subj, paste0(var, "_uni_sham")] <- uni_val - sham_val
      }
    }
  }

  return(delta_df)
}
```

```{r}
# Function to prepare regression data
prepare_regression_data <- function(caps_df, behavior_df, cap_vars, behavior_vars) {
  # Merge the datasets
  merged_data <- merge(caps_df, behavior_df, by = c("subject", "session"))

  # Create wide format for regression analysis
  wide_data <- merged_data %>%
    pivot_wider(
      id_cols = subject,
      names_from = session,
      values_from = all_of(c(cap_vars, behavior_vars)),
      names_sep = "_"
    )

  return(wide_data)
}
```

## Partial Corr Func

```{r}
library(ppcor)

# Function to run partial correlations between CAP and behavioral variables
# Controls for BOTH baseline behavior and baseline CAP
run_partial_corr <- function(wide_data, cap_var, behavior_vars,
                             condition = "bilateral", method = "spearman") {

  results_list <- list()

  for (behavior_var in behavior_vars) {
    # Define column names based on condition
    if (condition == "bilateral") {
      cap_col <- paste0(cap_var, "_Bilateral")
      behavior_col <- paste0(behavior_var, "_Bilateral")
    } else if (condition == "unilateral") {
      cap_col <- paste0(cap_var, "_Unilateral")
      behavior_col <- paste0(behavior_var, "_Unilateral")
    } else {
      next
    }

    baseline_behavior_col <- paste0(behavior_var, "_Sham")
    baseline_cap_col       <- paste0(cap_var, "_Sham")

    # Check if required columns exist and have sufficient data
    required_cols <- c(cap_col, behavior_col, baseline_behavior_col, baseline_cap_col)
    if (!all(required_cols %in% names(wide_data))) next

    # Remove rows with missing data ONLY (NO outlier removal)
    model_data <- wide_data[complete.cases(wide_data[required_cols]), ]
    if (nrow(model_data) < 5) next

    n_obs <- nrow(model_data)

    # Prepare data for ppcor
    # x = CAP (stim), y = behavior (stim), z = covariates (baseline behavior + baseline CAP)
    pcor_data <- data.frame(
      cap_stim     = model_data[[cap_col]],
      behav_stim   = model_data[[behavior_col]],
      behav_sham   = model_data[[baseline_behavior_col]],
      cap_sham     = model_data[[baseline_cap_col]]
    )

    tryCatch({
      # Partial correlation: control for BOTH baseline behavior and baseline CAP
      pcor_result <- pcor.test(
        x = pcor_data$behav_stim,
        y = pcor_data$cap_stim,
        z = pcor_data[, c("behav_sham", "cap_sham")],
        method = method
      )

      # Raw correlations for context
      raw_cap_behavior       <- cor.test(pcor_data$cap_stim,   pcor_data$behav_stim, method = method)
      raw_cap_baseBehavior   <- cor.test(pcor_data$cap_stim,   pcor_data$behav_sham, method = method)
      raw_cap_baseCap        <- cor.test(pcor_data$cap_stim,   pcor_data$cap_sham,   method = method)
      raw_behavior_baseBehavior <- cor.test(pcor_data$behav_stim, pcor_data$behav_sham, method = method)
      raw_behavior_baseCap      <- cor.test(pcor_data$behav_stim, pcor_data$cap_sham,   method = method)
      raw_baseBehavior_baseCap  <- cor.test(pcor_data$behav_sham, pcor_data$cap_sham,   method = method)

      partial_corr <- pcor_result$estimate
      r_squared <- partial_corr^2

      results_list[[behavior_var]] <- list(
        partial_correlation = partial_corr,
        t_statistic = pcor_result$statistic,
        p_value = pcor_result$p.value,
        r_squared = r_squared,
        n_obs = n_obs,
        condition = condition,
        cap_var = cap_var,
        behavior_var = behavior_var,
        method = method,
        raw_correlations = list(
          cap_behavior            = raw_cap_behavior$estimate,
          cap_vs_baselineBehavior = raw_cap_baseBehavior$estimate,
          cap_vs_baselineCap      = raw_cap_baseCap$estimate,
          behavior_vs_baselineBehavior = raw_behavior_baseBehavior$estimate,
          behavior_vs_baselineCap      = raw_behavior_baseCap$estimate,
          baselineBehavior_vs_baselineCap = raw_baseBehavior_baseCap$estimate
        ),
        ppcor_result = pcor_result  # full result for reference
      )
    }, error = function(e) {
      warning(paste("Error calculating partial correlation for", behavior_var,
                    "in", condition, "condition:", e$message))
    })
  }

  return(results_list)
}
```



```{r}
# Function to print partial correlation results summary
print_partial_corr_summary <- function(results_list, task_name, condition, cap_metric) {
  cat(strrep("=", 60), "\n")
  cat(toupper(task_name), "-", toupper(condition), "CONDITION -", toupper(cap_metric), "- PARTIAL CORRELATIONS\n")
  cat(strrep("=", 60), "\n")
  
  if (length(results_list) > 0) {
    cat("\nSignificant partial correlations (controlling for baseline behavior and CAP):\n")
    cat(strrep("-", 50), "\n")
    
    for (param in names(results_list)) {
      result <- results_list[[param]]
      
      # Determine significance level
      if (result$p_value < 0.001) {
        sig_level <- "***"
      } else if (result$p_value < 0.01) {
        sig_level <- "**"
      } else if (result$p_value < 0.051) {
        sig_level <- "*"
      } else {
        sig_level <- ""
      }
      
      # NO outlier info in output
      cat(sprintf("• %s: ρ=%.3f%s, p=%.3f, r²=%.3f, n=%d\n", 
                  param, 
                  result$partial_correlation,
                  sig_level,
                  result$p_value,
                  result$r_squared,
                  result$n_obs))
      
      # Print raw correlations for context
      cat(sprintf("  Raw: CAP-Behavior=%.3f, CAP-Baseline=%.3f, Behavior-Baseline=%.3f\n",
                  result$raw_correlations$cap_behavior,
                  result$raw_correlations$cap_vs_baselineBehavior,
                  result$raw_correlations$behavior_vs_baselineBehavior))
    }
  } else {
    cat("\nNo significant partial correlations found.\n")
  }
  
  cat("\n")
}

# Function to summarize significant partial correlation results
summarize_significant_partial_corr <- function(results_list, alpha = 0.05) {
  significant_results <- list()
  
  for (behavior_var in names(results_list)) {
    result <- results_list[[behavior_var]]
    
    # Check if partial correlation is significant
    if (result$p_value < alpha) {
      significant_results[[behavior_var]] <- result
    }
  }
  
  return(significant_results)
}
```


```{r}
library(dotenv)
load_dot_env(file = "../.env")

BASE_DIR          <- Sys.getenv("BASE_DIR")
RESULTS_DIR       <- Sys.getenv("RESULTS_DIR")
BEH_DATA_ANON_DIR <- Sys.getenv("BEH_DATA_ANON_DIR")

INPUT_DIR_BEH  <- file.path(BEH_DATA_ANON_DIR, "csv")
INPUT_DIR_CAPS <- file.path(BASE_DIR)

OUTPUT_DIR       <- file.path(RESULTS_DIR, "stats", "03_caps_beh")
PLOTS_OUTPUT_DIR <- file.path(RESULTS_DIR, "main_figures", "06_caps_beh")

dir.create(OUTPUT_DIR,       recursive = TRUE, showWarnings = FALSE)
dir.create(PLOTS_OUTPUT_DIR, recursive = TRUE, showWarnings = FALSE)
```

# Load CPAs data

```{r}
k=7
k7_df_occ <- prepare_df(file.path(INPUT_DIR_CAPS, "caps_dynamics_run-ON", 
                                 paste0("caps_nclust-", k), "CAP_occurence_times.csv"))

k7_df_dt <- prepare_df(file.path(INPUT_DIR_CAPS, "caps_dynamics_run-ON", 
                                paste0("caps_nclust-", k), "CAP_dwelltime.csv"))

str(k7_df_occ)
head(k7_df_occ)

str(k7_df_dt)
head(k7_df_dt)
```

# Load CPAs transition prob data
```{r}
cap_tp_full <- prepare_df(file.path(INPUT_DIR_CAPS, "caps_dynamics_run-ON",
                                "caps_nclust-7", "CAP_transitions_full.csv"))

str(cap_tp_full)
head(cap_tp_full)
```

```{r}
cap_tp_1_7 <- cap_tp_full %>% filter(from_CAP=="CAP1" & to_CAP=="CAP7")

str(cap_tp_1_7)
head(cap_tp_1_7)
```


```{r}
corr_method = "spearman"
```

## APM 


Left hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH, "APM_left_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH, "APM_left_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH, "APM_left_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()
comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))
comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  abs_error_x_m,
                                  abs_error_y_m,
                                  variability_x_m,
                                  variability_y_m,
                                  contraction_expansion_ratio_x,
                                  contraction_expansion_ratio_y,
                                  shift_x_m,
                                  shift_y_m)


# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_l <- comb_data
table(comb_data_l$stimulation_condition)
head(comb_data_l)
```

Righ hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"APM_right_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"APM_right_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"APM_right_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()
comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))



comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  abs_error_x_m,
                                  abs_error_y_m,
                                  variability_x_m,
                                  variability_y_m,
                                  contraction_expansion_ratio_x,
                                  contraction_expansion_ratio_y,
                                  shift_x_m,
                                  shift_y_m)


#co# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_r <- comb_data
table(comb_data_r$stimulation_condition)
head(comb_data_r)
```

```{r}
conatinated_apm <- rbind(comb_data_l, comb_data_r)
head(conatinated_apm)
tail(conatinated_apm)
str(conatinated_apm)
```

```{r}
apm_wide <- conatinated_apm %>%
  mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH")) %>%
  pivot_wider(
    id_cols = c("subject", "neuron_id", "handedness", "session"),
    names_from = arm_prefix,
    values_from = c(
      "fraction_complete",
      "abs_error_x_m",
      "abs_error_y_m",
      "variability_x_m",
      "variability_y_m",
      "contraction_expansion_ratio_x",
      "contraction_expansion_ratio_y",
      "shift_x_m",
      "shift_y_m"
    ),
    names_glue = "{arm_prefix}_{.value}"
  )

str(apm_wide)

head(apm_wide)
```

```{r, results='hide'}
cap_vars <- c("CAP4")

apm_behavior_vars <- c(
  "abs_error_x_m",
  "abs_error_y_m",
  "variability_x_m",
  "variability_y_m",
  "contraction_expansion_ratio_x",
  "contraction_expansion_ratio_y",
  "shift_x_m",
  "shift_y_m")

apm_behavior_vars_lh <- paste0("LH_", apm_behavior_vars)
apm_behavior_vars_rh <- paste0("RH_", apm_behavior_vars)

# Combine both LH and RH behavior variables
apm_behavior_vars_both_hands <- c(apm_behavior_vars_lh, apm_behavior_vars_rh)
```


## Occurance rate

```{r}
apm_occ_wide <- prepare_regression_data(k7_df_occ, apm_wide, "CAP4", apm_behavior_vars_both_hands)

# APM Occurrence Rate - Bilateral
apm_occ_bilateral_corr <- run_partial_corr(apm_occ_wide, "CAP4", apm_behavior_vars_both_hands, "bilateral", method = corr_method)
apm_occ_bilateral_sig <- summarize_significant_partial_corr(apm_occ_bilateral_corr)
print_partial_corr_summary(apm_occ_bilateral_sig, "APM", "BILATERAL", "OCCURRENCE RATE")

```


## Transition Probability

```{r}
cap_var = "transition_probability"

apm_tp_wide <- prepare_regression_data(cap_tp_1_7, apm_wide, cap_var, apm_behavior_vars_both_hands)

# APM Transition Probability - Bilateral
apm_tp_bilateral_corr <- run_partial_corr(apm_tp_wide, cap_var, apm_behavior_vars_both_hands, "bilateral", method = corr_method)
apm_tp_bilateral_sig <- summarize_significant_partial_corr(apm_tp_bilateral_corr)
print_partial_corr_summary(apm_tp_bilateral_sig, "APM", "BILATERAL", "Transition Probability")

```


# VGR 

Left hand
```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_left_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_left_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_left_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)


comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  posture_speed_m_s,
                                  reaction_time_s,
                                  initial_direction_angle_rad,
                                  initial_distance_ratio,
                                  speed_maxima_count,
                                  movement_time_s,
                                  path_length_ratio,
                                  false_starts)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_l <- comb_data
# Verifying the result
table(comb_data_l$stimulation_condition, comb_data_l$session)
head(comb_data_l)
```

Right hand

```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_right_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_right_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"VGR_right_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  posture_speed_m_s,
                                  reaction_time_s,
                                  initial_direction_angle_rad,
                                  initial_distance_ratio,
                                  speed_maxima_count,
                                  movement_time_s,
                                  path_length_ratio,
                                  false_starts)


comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

comb_data_r <- comb_data
# Verifying the result
table(comb_data_r$stimulation_condition, comb_data_r$session)
head(comb_data_r)
```

```{r}
conatinated_vgr <- rbind(comb_data_l, comb_data_r)
head(conatinated_vgr)
tail(conatinated_vgr)
table(conatinated_vgr$active_arm, conatinated_vgr$session)
```

```{r}
vgr_wide <- conatinated_vgr %>%
  mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH")) %>%
  pivot_wider(
    id_cols = c("subject", "neuron_id", "handedness", "session"),
    names_from = arm_prefix,
    values_from = c("fraction_complete",
                    "posture_speed_m_s",
                    "reaction_time_s",
                    "initial_direction_angle_rad",
                    "initial_distance_ratio",
                    "speed_maxima_count",
                    "movement_time_s",
                    "path_length_ratio",
                    "false_starts"
    ),
    names_glue = "{arm_prefix}_{.value}"
  )

str(vgr_wide)

head(vgr_wide)
```

```{r, results='hide'}
cap_vars <- c("CAP4")
vgr_behavior_vars <- c("posture_speed_m_s", 
                       "reaction_time_s", 
                       "initial_direction_angle_rad", 
                       "initial_distance_ratio", 
                       "speed_maxima_count",
                       "movement_time_s", 
                       "path_length_ratio", 
                       "false_starts")

vgr_behavior_vars_lh <- paste0("LH_", vgr_behavior_vars)
vgr_behavior_vars_rh <- paste0("RH_", vgr_behavior_vars)

# Combine both LH and RH behavior variables
vgr_behavior_vars_both_hands <- c(vgr_behavior_vars_lh, vgr_behavior_vars_rh)
```


## Occurance rate

```{r}
vgr_occ_wide <- prepare_regression_data(k7_df_occ, vgr_wide, "CAP4", vgr_behavior_vars_both_hands)

# VGR Occurrence Rate - Bilateral
vgr_occ_bilateral_corr <- run_partial_corr(vgr_occ_wide, "CAP4", vgr_behavior_vars_both_hands, "bilateral", method = corr_method)
vgr_occ_bilateral_sig <- summarize_significant_partial_corr(vgr_occ_bilateral_corr)
print_partial_corr_summary(vgr_occ_bilateral_sig, "VGR", "BILATERAL", "OCCURRENCE RATE")

```

## Transition Probability

```{r}
cap_var = "transition_probability"

vgr_tp_wide <- prepare_regression_data(cap_tp_1_7, vgr_wide, cap_var, vgr_behavior_vars_both_hands)

# VGR Transition Probability - Bilateral
vgr_tp_bilateral_corr <- run_partial_corr(vgr_tp_wide, cap_var, vgr_behavior_vars_both_hands, "bilateral", method = corr_method)
vgr_tp_bilateral_sig <- summarize_significant_partial_corr(vgr_tp_bilateral_corr)
print_partial_corr_summary(vgr_tp_bilateral_sig, "VGR", "BILATERAL", "Transition Probability")

```

# OH
```{r, results='hide'}
bi_data <- read.csv(file.path(INPUT_DIR_BEH,"OH_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"OH_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"OH_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete,
                                  handedness, stimulation_condition, active_arm,
                                  total_hits,
                                  hits_with_left,
                                  hits_with_right,
                                  hand_bias_of_hits,
                                  median_error,
                                  miss_bias,
                                  hand_speed_right_m_s,
                                  hand_speed_left_m_s,
                                  hand_speed_bias,
                                  movement_area_right_hand_m_2, 
                                  movement_area_left_hand_m_2,
                                  movement_area_bias,
                                  hand_transition,
                                  hand_selection_overlap)


comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

# Verifying the result
oh_data <- comb_data
table(oh_data$stimulation_condition, oh_data$session)
head(oh_data)
```
```{r}
cap_vars <- c("CAP4")
oh_behavior_vars <- c("total_hits", 
                   "hits_with_left", 
                   "hits_with_right", 
                   "hand_bias_of_hits",
                   "median_error", 
                   "miss_bias", 
                   "hand_speed_right_m_s",
                   "hand_speed_left_m_s", 
                   "hand_speed_bias", 
                   "movement_area_right_hand_m_2", 
                   "movement_area_left_hand_m_2", 
                   "movement_area_bias", 
                   "hand_transition",
                   "hand_selection_overlap")

```

## Occurance rate

```{r}
oh_occ_wide <- prepare_regression_data(k7_df_occ, oh_data, "CAP4", oh_behavior_vars)

# OH Occurrence Rate - Bilateral
oh_occ_bilateral_corr <- run_partial_corr(oh_occ_wide, "CAP4", oh_behavior_vars, "bilateral", method = corr_method)
oh_occ_bilateral_sig <- summarize_significant_partial_corr(oh_occ_bilateral_corr)
print_partial_corr_summary(oh_occ_bilateral_sig, "OH", "BILATERAL", "OCCURRENCE RATE")

```


## Transition Probability

```{r}
cap_var = "transition_probability"

oh_tp_wide <- prepare_regression_data(cap_tp_1_7, oh_data, cap_var, oh_behavior_vars)

# OH Transition Probability - Bilateral
oh_tp_bilateral_corr <- run_partial_corr(oh_tp_wide, cap_var, oh_behavior_vars, "bilateral", method = corr_method)
oh_tp_bilateral_sig <- summarize_significant_partial_corr(oh_tp_bilateral_corr)
print_partial_corr_summary(oh_tp_bilateral_sig, "OH", "BILATERAL", "Transition Probability")

```

# BOB

```{r, results='hide'}

bi_data <- read.csv(file.path(INPUT_DIR_BEH,"BOB_bi.csv"), check.names=TRUE)
bi_data <- bi_data %>% clean_names()

ua_data <- read.csv(file.path(INPUT_DIR_BEH,"BOB_ua.csv"), check.names=TRUE)
ua_data <- ua_data %>% clean_names()

sham_data <- read.csv(file.path(INPUT_DIR_BEH,"BOB_sham.csv"), check.names=TRUE)
sham_data <- sham_data %>% clean_names()

comb_data <- rbind(ua_data, bi_data, sham_data)

## Choose only young participants
comb_data <- comb_data[startsWith(as.character(comb_data$neuron_id), 'Y_'),]

## Factorial variables
comb_data$stimulation_condition <- factor(comb_data$stimulation_condition)
comb_data$active_arm <- factor(comb_data$active_arm)
comb_data$session_no <- ordered(comb_data$session_no, levels=c(1, 2, 3))

comb_data <- comb_data %>% dplyr::select(neuron_id, session_no, fraction_complete, handedness,
                                  stimulation_condition, active_arm,
                                  x1_targets_completed,
                                  x2_targets_completed,
                                  x3_targets_completed,
                                  #x2_drops,#variance=0
                                  x3_drops,#
                                  #x2_drops_targets,##variance=0
                                  x3_drops_targets,#
                                  x1_mean_movement_time_s,
                                  x2_mean_movement_time_s,
                                  x3_mean_movement_time_s,
                                  x1_right_hand_speed_maxima,
                                  x2_right_hand_speed_maxima,
                                  x3_right_hand_speed_maxima,
                                  x1_left_hand_speed_maxima,
                                  x2_left_hand_speed_maxima,
                                  x3_left_hand_speed_maxima,
                                  x1_mean_bar_angle_rad,
                                  x2_mean_bar_angle_rad,
                                  x3_mean_bar_angle_rad,
                                  x1_bar_length_variability,#
                                  x2_bar_length_variability,#
                                  x3_bar_length_variability,#
                                  x1_reaction_time_abs_diff_s,
                                  x1_hand_speed_diff_m_s,
                                  x2_hand_speed_diff_m_s,
                                  x3_hand_speed_diff_m_s,
                                  x1_mean_right_hand_speed_m_s,
                                  x2_mean_right_hand_speed_m_s, 
                                  x3_mean_right_hand_speed_m_s,
                                  x1_mean_left_hand_speed_m_s,
                                  x2_mean_left_hand_speed_m_s, 
                                  x3_mean_left_hand_speed_m_s, 
                                  x1_mean_bar_angle_rad,
                                  x2_mean_bar_angle_rad,
                                  x3_mean_bar_angle_rad,
                                  x1_stdev_bar_angle_rad,
                                  x2_stdev_bar_angle_rad,
                                  x3_stdev_bar_angle_rad,
                                  x1_norm_absolute_hand_speed_diff,
                                  x2_norm_absolute_hand_speed_diff,
                                  x3_norm_absolute_hand_speed_diff,
                                  x1_hand_speed_peak_bias,
                                  x2_hand_speed_peak_bias,
                                  x3_hand_speed_peak_bias,
                                  x1_hand_path_bias,
                                  x2_hand_path_bias,
                                  x3_hand_path_bias 
                                  )

bob_behavior_vars <- c(
  "x1_targets_completed",
  "x2_targets_completed",
  "x3_targets_completed",
  #"x2_drops", #variance=0
  "x3_drops",
  #"x2_drops_targets", #variance=0
  "x3_drops_targets",
  "x1_mean_movement_time_s",
  "x2_mean_movement_time_s",
  "x3_mean_movement_time_s",
  "x1_right_hand_speed_maxima",
  "x2_right_hand_speed_maxima",
  "x3_right_hand_speed_maxima",
  "x1_left_hand_speed_maxima",
  "x2_left_hand_speed_maxima",
  "x3_left_hand_speed_maxima",
  "x1_mean_bar_angle_rad",
  "x2_mean_bar_angle_rad",
  "x3_mean_bar_angle_rad",
  "x1_bar_length_variability",
  "x2_bar_length_variability",
  "x3_bar_length_variability",
  "x1_reaction_time_abs_diff_s",
  "x1_hand_speed_diff_m_s",
  "x2_hand_speed_diff_m_s",
  "x3_hand_speed_diff_m_s", 
  "x1_mean_right_hand_speed_m_s",
  "x2_mean_right_hand_speed_m_s", 
  "x3_mean_right_hand_speed_m_s",
  "x1_mean_left_hand_speed_m_s",
  "x2_mean_left_hand_speed_m_s", 
  "x3_mean_left_hand_speed_m_s",
  "x1_mean_bar_angle_rad",
  "x2_mean_bar_angle_rad",
  "x3_mean_bar_angle_rad",
  "x1_stdev_bar_angle_rad",
  "x2_stdev_bar_angle_rad",
  "x3_stdev_bar_angle_rad",
  "x1_norm_absolute_hand_speed_diff",
  "x2_norm_absolute_hand_speed_diff",
  "x3_norm_absolute_hand_speed_diff",
  "x1_hand_speed_peak_bias",
  "x2_hand_speed_peak_bias",
  "x3_hand_speed_peak_bias",
  "x1_hand_path_bias",
  "x2_hand_path_bias",
  "x3_hand_path_bias" 
)

# Convert all numeric variables
comb_data <- comb_data %>%
  mutate(across(all_of(bob_behavior_vars), as.numeric))

comb_data <- comb_data %>%
  mutate(subject = gsub("_", "", neuron_id))

comb_data$session <- as.character(comb_data$stimulation_condition)

# Applying the mappings
comb_data$session[comb_data$session == "bi-tDCS"] <- "Bilateral"
comb_data$session[comb_data$session == "sham"] <- "Sham"
comb_data$session[comb_data$session == "ua-tDCS"] <- "Unilateral"
comb_data$session <- factor(comb_data$session, levels = c("Sham", "Unilateral", "Bilateral"))

bob_data <- comb_data
# Verifying the result
table(bob_data$stimulation_condition,bob_data$session)
head(bob_data)
```

## Occurance rate


```{r}
bob_occ_wide <- prepare_regression_data(k7_df_occ, bob_data, "CAP4", bob_behavior_vars)

# BOB Occurrence Rate - Bilateral
bob_occ_bilateral_corr <- run_partial_corr(bob_occ_wide, "CAP4", bob_behavior_vars, "bilateral", method = corr_method)
bob_occ_bilateral_sig <- summarize_significant_partial_corr(bob_occ_bilateral_corr)
print_partial_corr_summary(bob_occ_bilateral_sig, "BOB", "BILATERAL", "OCCURRENCE RATE")

```



## Transition Probability

```{r}
cap_var = "transition_probability"

bob_tp_wide <- prepare_regression_data(cap_tp_1_7, bob_data, cap_var, bob_behavior_vars)

# BOB Transition Probability - Bilateral
bob_tp_bilateral_corr <- run_partial_corr(bob_tp_wide, cap_var, bob_behavior_vars, "bilateral", method = corr_method)
bob_tp_bilateral_sig <- summarize_significant_partial_corr(bob_tp_bilateral_corr)
print_partial_corr_summary(bob_tp_bilateral_sig, "BOB", "BILATERAL", "Transition Probability")

```


## Collect and save results

```{r}
# Function to extract ALL bilateral partial correlation results
extract_all_results <- function() {
  all_results <- data.frame()
  
  # Task-metric combinations to process
  tasks_metrics <- list(
    list(name = "APM", occ_bi = apm_occ_bilateral_corr,
         tp_bi = apm_tp_bilateral_corr),
    list(name = "VGR", occ_bi = vgr_occ_bilateral_corr,
         tp_bi = vgr_tp_bilateral_corr),
    list(name = "OH", occ_bi = oh_occ_bilateral_corr,
         tp_bi = oh_tp_bilateral_corr),
    list(name = "BOB", occ_bi = bob_occ_bilateral_corr,
         tp_bi = bob_tp_bilateral_corr)
  )

  # Process each task
  for (task_data in tasks_metrics) {
    task_name <- task_data$name

    # Process each metric
    metrics <- list(
      list(name = "CAP4 Occurrence Rate", bi = task_data$occ_bi),
      list(name = "CAP1->CAP7 Transition Probability", bi = task_data$tp_bi)
    )

    for (metric_data in metrics) {
      metric_name <- metric_data$name

      # Get all parameters from bilateral
      all_params <- names(metric_data$bi)

      for (param_name in all_params) {
        # Process bilateral results
        bi_result <- metric_data$bi[[param_name]]
        if (!is.null(bi_result)) {
          all_results <- rbind(all_results, data.frame(
            task = task_name,
            metric = metric_name,
            condition = "Bilateral",
            parameter = param_name,
            correlation = bi_result$partial_correlation,
            p_value = bi_result$p_value,
            r_squared = bi_result$r_squared,
            n_obs = bi_result$n_obs,
            stringsAsFactors = FALSE
          ))
        }
      }
    }
  }
  
  return(all_results)
}
all_results <- extract_all_results()


all_results <- all_results %>%
  mutate(sig = case_when(
    p_value < 0.001 ~ "***",
    p_value < 0.01  ~ "**",
    p_value < 0.05  ~ "*",
    TRUE            ~ ""
  )) %>%
  arrange(p_value)

write.csv(all_results, file.path(OUTPUT_DIR, "bilateral_partial_corr_data.csv"), row.names = FALSE)
```



