---
title: "Revision check 01: Sample-size sensitivity"
output:
  html_document:
    toc: false
    number_sections: false
date: "2026-08-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Purpose

Estimate the minimum detectable effect for the primary three-condition within-participant comparison.

The manuscript uses permutation-based omnibus tests. This notebook uses the corresponding parametric repeated-measures F test as an approximate benchmark of design sensitivity.

G\*Power: <https://www.psychologie.hhu.de/arbeitsgruppen/allgemeine-psychologie-und-arbeitspsychologie/gpower>

# Assumptions

- Sensitivity analysis: sample size, alpha, and target power are fixed; effect size is solved for.
- Participants: `N = 20`
- Groups: `1`
- Repeated measurements: `3`
- Alpha: `0.05`
- Target power: `0.80`
- Correlation among repeated measurements: `rho = 0.50` (assumed moderate correlation)
- Nonsphericity correction: `epsilon = 1` (sphericity assumed)
- Effect-size parameterization follows the standard G\*Power repeated-measures specification.

# Sensitivity calculation

```{r sensitivity}
N <- 20
K <- 3
ALPHA <- 0.05
TARGET_POWER <- 0.80
RHO <- 0.50
EPSILON <- 1

# Degrees of freedom for the within-participant omnibus F test.
df1 <- (K - 1) * EPSILON
df2 <- (N - 1) * (K - 1) * EPSILON
critical_F <- qf(1 - ALPHA, df1, df2)

# Standard repeated-measures parameterization used by G*Power.
power_for_f <- function(f) {
  lambda <- N * K * f^2 / (1 - RHO)
  1 - pf(critical_F, df1, df2, ncp = lambda)
}

f_min <- uniroot(
  function(f) power_for_f(f) - TARGET_POWER,
  interval = c(1e-4, 2)
)$root

result <- data.frame(
  N = N,
  measurements = K,
  alpha = ALPHA,
  target_power = TARGET_POWER,
  rho = RHO,
  epsilon = EPSILON,
  minimum_detectable_f = round(f_min, 3),
  achieved_power = round(power_for_f(f_min), 3)
)

knitr::kable(result)
```

# Interpretation

Under these assumptions, the minimum detectable effect is approximately **Cohen's f = 0.295 (about 0.30)** at 80% power.

Because the manuscript's primary omnibus test is permutation-based, this value is used as an approximate sensitivity benchmark rather than an exact power calculation for the permutation test.

# Reference

Faul, F., Erdfelder, E., Lang, A.-G., & Buchner, A. (2007). G\*Power 3: A flexible statistical power analysis program for the social, behavioral, and biomedical sciences. Behavior Research Methods, 39(2), 175–191. https://doi.org/10.3758/BF03193146
