---
title: "Revision check 02: Session-order (learning) effects table"
output:
  html_document:
    toc: false
    number_sections: false
date: "2026-09-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Purpose

Table of the behavioral parameters with a significant session-order (learning) effect (p < 0.05). Stats come from `02_statistical_analysis_behavioral_tasks.Rmd` (`learning_effect_all_tasks.csv`); session means are computed here. Saved as a CSV in `revision_checks/`.

# Paths

```{r paths}
library(dplyr)
library(janitor)
library(knitr)
library(dotenv)

# Repo root .env is two levels up from revision_checks/ (one up if knitting from stats_and_R_figures/)
env_path <- if (file.exists("../../.env")) "../../.env" else "../.env"
load_dot_env(file = env_path)

RESULTS_DIR       <- Sys.getenv("RESULTS_DIR")
BEH_DATA_ANON_DIR <- Sys.getenv("BEH_DATA_ANON_DIR")

LEARNING_CSV <- file.path(RESULTS_DIR, "stats", "01_behavioral_tasks", "learning_effect_all_tasks.csv")
INPUT_DIR    <- file.path(BEH_DATA_ANON_DIR, "csv")
OUT_CSV      <- "02_learning_effect_significant_params.csv"
```

# Significant learning effects

```{r load-results}
all_learning <- read.csv(LEARNING_CSV, check.names = FALSE)

sig <- all_learning %>%
  filter(p_value < 0.05) %>%
  distinct(task, parameter, .keep_all = TRUE)

cat("Significant parameters (expected 19):", nrow(sig), "\n")
table(sig$task)
```

# Behavioral data

Same loading and filtering as notebook 02: combine the three condition CSVs per task, keep only young participants (`Y_` prefix), sessions ordered 1-3. For APM/VGR the LH/RH prefix in the parameter name maps to `active_arm`.

```{r load-data}
load_task_csvs <- function(files) {
  dfs <- lapply(files, function(f) clean_names(read.csv(file.path(INPUT_DIR, f), check.names = TRUE)))
  comb <- bind_rows(dfs)
  comb <- comb[startsWith(as.character(comb$neuron_id), "Y_"), ]
  comb$session_no <- ordered(comb$session_no, levels = c(1, 2, 3))
  comb
}

apm_long <- bind_rows(
  load_task_csvs(c("APM_left_bi.csv", "APM_left_ua.csv", "APM_left_sham.csv")),
  load_task_csvs(c("APM_right_bi.csv", "APM_right_ua.csv", "APM_right_sham.csv"))
) %>% mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH"))

vgr_long <- bind_rows(
  load_task_csvs(c("VGR_left_bi.csv", "VGR_left_ua.csv", "VGR_left_sham.csv")),
  load_task_csvs(c("VGR_right_bi.csv", "VGR_right_ua.csv", "VGR_right_sham.csv"))
) %>% mutate(arm_prefix = ifelse(active_arm == "LEFT", "LH", "RH"))

bob_data <- load_task_csvs(c("BOB_bi.csv", "BOB_ua.csv", "BOB_sham.csv"))
oh_data  <- load_task_csvs(c("OH_bi.csv", "OH_ua.csv", "OH_sham.csv"))

# Notebook 02 coerces BOB parameters to numeric; do the same for the ones we need
bob_params <- unique(sig$parameter[sig$task == "BOB"])
bob_data <- bob_data %>% mutate(across(all_of(bob_params), ~ suppressWarnings(as.numeric(.x))))

task_data <- list(APM = apm_long, VGR = vgr_long, BOB = bob_data, OH = oh_data)
```

# Session means

Mean of each parameter per session (1, 2, 3), pooled across stimulation conditions, missing values dropped (as in the LMER fits).

```{r session-means}
session_means_text <- function(df, param) {
  # LH_/RH_ prefixed parameters (APM, VGR): filter the matching arm, use the base column
  if (grepl("^(LH|RH)_", param) && "arm_prefix" %in% names(df)) {
    df <- df[df$arm_prefix == substr(param, 1, 2), ]
    param <- sub("^(LH|RH)_", "", param)
  }
  m <- df %>%
    filter(!is.na(.data[[param]])) %>%
    group_by(session_no) %>%
    summarise(m = mean(.data[[param]]), .groups = "drop") %>%
    arrange(session_no)
  paste(signif(m$m, 3), collapse = " -> ")
}

sig <- sig %>%
  rowwise() %>%
  mutate(session_means = session_means_text(task_data[[task]], parameter)) %>%
  ungroup()
```

# Build and save table

```{r final-table}
format_df2 <- function(x) {
  ifelse(abs(x - round(x)) < 0.01, sprintf("%d", round(x)), sprintf("%.2f", x))
}

final_table <- sig %>%
  mutate(task = factor(task, levels = c("APM", "VGR", "BOB", "OH"))) %>%
  arrange(task, p_value) %>%
  transmute(
    Task = as.character(task),
    Parameter = parameter,
    `F(df1, df2)` = sprintf("F(%d, %s) = %.2f", df_num, format_df2(df_denom), f_statistic),
    `p value` = ifelse(p_value < 0.001, "< 0.001", sprintf("%.3f", p_value)),
    `Session means (S1 -> S2 -> S3)` = session_means
  )

write.csv(final_table, OUT_CSV, row.names = FALSE)
cat("Saved:", OUT_CSV, "\n")

kable(final_table)
```
